---
title: "Network Benchmark Analysis"
params:
  result_id: "all"
  note: null
  config_file: null
output:
  html_document:
    toc: true
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 13, fig.height = 7)

rmd_dir <- dirname(normalizePath(knitr::current_input(dir = TRUE)))
repo_root <- normalizePath(file.path(rmd_dir, "..", ".."))

source(file.path(repo_root, "analysis", "network", "prelude.r"))
options(scipen = 999)

result_id <- params$result_id
results_dir <- file.path(repo_root, "analysis", "network", result_id)

required_csvs <- c(
  "network_scenarios.csv",
  "network_iperf3.csv",
  "network_iperf3_intervals.csv",
  "network_sockperf.csv"
)

if (!all(file.exists(file.path(results_dir, required_csvs)))) {
  source(file.path(repo_root, "analysis", "network", "build_csv.R"), local = TRUE)
  write_network_csvs(repo_root = repo_root, run_spec = result_id)
}

csv_sql_path <- function(name) {
  gsub("'", "''", normalizePath(file.path(results_dir, name), mustWork = TRUE), fixed = TRUE)
}

sql("select 1")
con <- duckdbcons[[":memory:"]]
DBI::dbExecute(con, "drop table if exists scenarios")
DBI::dbExecute(con, "drop table if exists iperf3")
DBI::dbExecute(con, "drop table if exists iperf3_intervals")
DBI::dbExecute(con, "drop table if exists sockperf")
DBI::dbExecute(con, sprintf("create table scenarios_all as select * from read_csv_auto('%s')", csv_sql_path("network_scenarios.csv")))
DBI::dbExecute(con, sprintf("create table iperf3_all as select * from read_csv_auto('%s')", csv_sql_path("network_iperf3.csv")))
DBI::dbExecute(con, sprintf("create table iperf3_intervals_all as select * from read_csv_auto('%s')", csv_sql_path("network_iperf3_intervals.csv")))
DBI::dbExecute(con, sprintf("create table sockperf_all as select * from read_csv_auto('%s')", csv_sql_path("network_sockperf.csv")))

# read_csv_auto infers a column's type from its values, so a numeric column that
# happens to be entirely empty in this result set arrives as VARCHAR and any
# arithmetic on it fails with a binder error. That is the normal state of a newly
# added measurement before the first run that populates it. Declare the columns
# that are numeric by contract and coerce them regardless of what was inferred.
quote_sql_literal <- function(x) paste0("'", gsub("'", "''", x, fixed = TRUE), "'")

ensure_numeric_columns <- function(table, cols) {
  existing <- DBI::dbGetQuery(con, sprintf(
    "select column_name, data_type from information_schema.columns where table_name = %s",
    quote_sql_literal(table)
  ))
  for (col in intersect(cols, existing$column_name)) {
    if (!identical(existing$data_type[existing$column_name == col], "DOUBLE")) {
      DBI::dbExecute(con, sprintf('alter table %s alter column "%s" type double', table, col))
    }
  }
}

ensure_numeric_columns("sockperf_all", c(
  "offered_mps", "achieved_mps", "burst", "reply_every",
  "msg_size_bytes", "configured_runtime_sec", "runtime_sec", "warmup_msec",
  "valid_duration_sec", "sent_messages", "received_messages",
  "avg_rtt_us", "stddev_rtt_us", "min_rtt_us", "max_rtt_us",
  "p25_rtt_us", "p50_rtt_us", "p75_rtt_us", "p90_rtt_us",
  "p99_rtt_us", "p999_rtt_us", "p9999_rtt_us", "p99999_rtt_us",
  "dropped_messages", "duplicated_messages", "out_of_order_messages"
))

# The iperf3 tables need the same treatment, and for a reason that is now the
# common case rather than a corner one: a run of the latency-vs-rate ladder
# produces no iperf3 rows at all, so every scenario in the TCP-vs-UDP study
# writes a header-only network_iperf3.csv. Without this, every iperf3 section
# fails to bind -- round(VARCHAR, INTEGER) -- and takes the whole report with
# it, including the sockperf sections that do have data.
ensure_numeric_columns("iperf3_all", c(
  "runtime_sec", "omit_sec", "parallel_streams",
  "tcp_length_bytes",
  "udp_target_bitrate_bits_per_sec", "udp_target_bitrate_gbit_per_sec",
  "udp_length_bytes",
  "sender_mbit_per_sec", "receiver_mbit_per_sec",
  "sender_bytes", "receiver_bytes", "retransmits",
  "jitter_ms", "lost_packets", "packets", "lost_percent",
  "cpu_host_total_pct", "cpu_host_user_pct", "cpu_host_system_pct",
  "cpu_remote_total_pct", "cpu_remote_user_pct", "cpu_remote_system_pct",
  "server_port", "timestamp_epoch"
))

ensure_numeric_columns("iperf3_intervals_all", c(
  "interval_index", "interval_start_sec", "interval_end_sec",
  "interval_seconds",
  "bits_per_second", "mbit_per_sec", "bytes", "packets", "retransmits",
  "jitter_ms", "lost_packets", "lost_percent"
))
numeric_scenario_cols <- c(
  "primary_iface_mtu", "cpu_idle_deep_entries_delta",
  "tuning_rmem_max", "tuning_netdev_max_backlog",
  "cpufreq_cur_freq_khz", "cpufreq_min_freq_khz", "cpufreq_max_freq_khz",
  "server_cpu_idle_deep_entries_delta", "server_primary_iface_mtu"
)
# The scenario columns are also carried on every measurement row, so the same
# coercion has to reach those tables or arithmetic on them breaks there instead.
ensure_numeric_columns("scenarios_all", numeric_scenario_cols)
ensure_numeric_columns("iperf3_all", numeric_scenario_cols)
ensure_numeric_columns("iperf3_intervals_all", numeric_scenario_cols)
ensure_numeric_columns("sockperf_all", numeric_scenario_cols)

# Every analysis query below reads these views, which exclude reversal-control
# arms. A control re-runs a scenario to measure drift; letting its rows into the
# comparisons would count that configuration twice and pull the median toward
# whatever the control happened to measure. The Data Quality section reads the
# *_all tables instead, because comparing the two is the whole point of it.
# Compared as text rather than as a boolean, because the column's type is not
# stable across result sets. read_csv_auto infers it from the data: BOOLEAN when
# rows are present, VARCHAR when the table is empty and every column is a bare
# header. `coalesce(is_control, false)` then binds fine on one directory and
# fails on another.
#
# An empty table here is normal, not exceptional: a run of the latency-vs-rate
# ladder produces no iperf3 rows at all, so every scenario in the TCP-vs-UDP
# study writes an empty network_iperf3.csv.
for (tbl in c("scenarios", "iperf3", "iperf3_intervals", "sockperf")) {
  DBI::dbExecute(con, sprintf(
    "create view %s as select * from %s_all where coalesce(lower(cast(is_control as varchar)), 'false') not in ('true', 't', '1')",
    tbl, tbl
  ))
}

# network_failures.csv is written by build_csv.R alongside the measurement
# tables. Older result directories predate it, so its absence is tolerated.
failures_csv <- file.path(results_dir, "network_failures.csv")
DBI::dbExecute(con, "drop table if exists failures")
if (file.exists(failures_csv)) {
  DBI::dbExecute(con, sprintf("create table failures as select * from read_csv_auto('%s')", csv_sql_path("network_failures.csv")))
} else {
  DBI::dbExecute(con, "create table failures (run_id varchar, scenario_name varchar, benchmark_name varchar, repetition double, failure_reason varchar)")
}

# Report constants, overridable with --config so a new provider or instance
# family does not require editing SQL throughout this document. Mirrors
# analysis/storage/storage_report_config.example.json.
default_report_config <- list(
  # Instance types used by the two placement comparisons.
  placement_comparison_small_machine = "g2a.2d",
  placement_comparison_large_machine = "g2a.120d",
  # Fixed points that keep like compared with like.
  reference_tcp_length_bytes = 131072,
  reference_udp_length_bytes = 1492,
  reference_udp_target_gbps = 90,
  reference_sockperf_msg_size_bytes = 64,
  reference_os_tuning = "standard",
  instance_comparison_placement_class = "different-host-single-az",
  # Admission rules for the under-load ladder.
  #
  # A rung whose generator fell short of its offered rate measures the
  # generator's ceiling, not the network's. 95% is loose enough to matter: TCP
  # is the arm more likely to fall short, latency-vs-rate is superlinear near
  # the knee, and the shortfall is largest exactly where the interesting
  # divergence lives -- so a loose filter systematically flatters TCP.
  ul_min_delivered_pct = 99,
  # Two arms only compare if they ran at the same *achieved* load. Equal
  # offered rate is not equal load once either arm misses its target.
  ul_max_rate_gap_pct = 2,
  # A percentile needs samples behind it. p99.9 estimated from a handful of
  # observations is noise with a precise-looking name.
  ul_min_tail_samples = 100,
  # Ordering only; values absent from the data are dropped.
  preferred_provider_order = c("stackit", "aws", "gcp"),
  preferred_placement_order = c(
    "co-located-single-az", "single-az", "different-host-single-az",
    "multi-az", "cross-region"
  )
)

merge_lists <- function(base, override) {
  for (key in names(override)) base[[key]] <- override[[key]]
  base
}

report_config <- default_report_config
if (!is.null(params$config_file) && nzchar(params$config_file)) {
  config_override <- jsonlite::fromJSON(params$config_file, simplifyDataFrame = TRUE)
  unknown_keys <- setdiff(names(config_override), names(default_report_config))
  if (length(unknown_keys) > 0) {
    stop(sprintf("Unknown network report config keys: %s", paste(unknown_keys, collapse = ", ")))
  }
  report_config <- merge_lists(report_config, config_override)
}

cfg <- function(key) report_config[[key]]
quote_sql <- function(x) as.character(DBI::dbQuoteString(con, as.character(x)))

# Bound once so every query below reads the same value and a --config override
# reaches all of them. Strings go through quote_sql; numbers are interpolated
# directly. Anything comparing against these must use sprintf rather than a
# literal, or the override silently applies to only part of the report.
small_machine <- cfg("placement_comparison_small_machine")
large_machine <- cfg("placement_comparison_large_machine")
ref_os_tuning <- cfg("reference_os_tuning")
ref_placement <- cfg("instance_comparison_placement_class")
ul_min_delivered <- cfg("ul_min_delivered_pct")
ul_max_rate_gap <- cfg("ul_max_rate_gap_pct")
ul_min_tail_samples <- cfg("ul_min_tail_samples")
ref_tcp_length_bytes <- cfg("reference_tcp_length_bytes")
ref_udp_length_bytes <- cfg("reference_udp_length_bytes")
ref_udp_target_gbps <- cfg("reference_udp_target_gbps")
ref_msg_size_bytes <- cfg("reference_sockperf_msg_size_bytes")

q_small <- quote_sql(small_machine)
q_large <- quote_sql(large_machine)
q_tuning <- quote_sql(ref_os_tuning)
q_placement <- quote_sql(ref_placement)

format_placement <- function(x) {
  factor(x, levels = placement_levels, labels = placement_labels[placement_levels])
}

no_data <- function(msg) {
  show_no_data_plot(msg)
}

box_label_accuracy <- function(values, percent = FALSE) {
  finite_values <- values[is.finite(values)]
  if (length(finite_values) == 0) return(1)
  max_abs <- max(abs(finite_values), na.rm = TRUE)
  if (percent) {
    if (max_abs >= 10) return(0.1)
    if (max_abs >= 1) return(0.01)
    return(0.001)
  }
  if (max_abs >= 1000) return(1)
  if (max_abs >= 100) return(0.1)
  if (max_abs >= 10) return(0.1)
  if (max_abs >= 1) return(0.01)
  if (max_abs >= 0.1) return(0.001)
  0.0001
}

format_box_median_labels <- function(values, y, ylab = NULL) {
  percent_metric <- identical(y, "lost_percent") || (!is.null(ylab) && grepl("%", ylab, fixed = TRUE))
  accuracy <- box_label_accuracy(values, percent = percent_metric)
  formatter <- if (percent_metric) {
    label_percent(scale = 1, accuracy = accuracy)
  } else {
    label_number(accuracy = accuracy, big.mark = ",", trim = TRUE)
  }
  formatter(values)
}

build_box_median_annotation <- function(df, x, y, fill = NULL, facet_cols = NULL, formatter = NULL,
                                        max_boxes_per_panel = 8, max_panels = 16, max_labels = 48) {
  required_cols <- unique(c(x, y, fill, facet_cols))
  plot_df <- df[stats::complete.cases(df[, required_cols, drop = FALSE]), required_cols, drop = FALSE]
  if (nrow(plot_df) == 0) return(list(enabled = FALSE, data = NULL, upper_expand = 0.06))

  group_cols <- unique(c(facet_cols, x, fill))
  split_key <- interaction(plot_df[, group_cols, drop = FALSE], drop = TRUE, lex.order = TRUE, sep = "\r")
  label_groups <- split(plot_df, split_key, drop = TRUE)
  label_rows <- lapply(label_groups, function(group_df) {
    row <- group_df[1, group_cols, drop = FALSE]
    row$median_value <- stats::median(group_df[[y]], na.rm = TRUE)
    row
  })
  label_df <- do.call(rbind, label_rows)
  rownames(label_df) <- NULL

  if (length(facet_cols) == 0) {
    label_df$panel_min <- min(plot_df[[y]], na.rm = TRUE)
    label_df$panel_max <- max(plot_df[[y]], na.rm = TRUE)
    panel_count <- 1L
    boxes_per_panel <- nrow(label_df)
  } else {
    panel_split_key <- interaction(plot_df[, facet_cols, drop = FALSE], drop = TRUE, lex.order = TRUE, sep = "\r")
    panel_groups <- split(plot_df, panel_split_key, drop = TRUE)
    panel_rows <- lapply(panel_groups, function(group_df) {
      row <- group_df[1, facet_cols, drop = FALSE]
      row$panel_min <- min(group_df[[y]], na.rm = TRUE)
      row$panel_max <- max(group_df[[y]], na.rm = TRUE)
      row
    })
    panel_range_df <- do.call(rbind, panel_rows)
    rownames(panel_range_df) <- NULL
    label_df <- merge(label_df, panel_range_df, by = facet_cols, sort = FALSE)
    panel_label_counts <- vapply(split(label_df, interaction(label_df[, facet_cols, drop = FALSE], drop = TRUE, lex.order = TRUE, sep = "\r")), nrow, integer(1))
    panel_count <- length(panel_label_counts)
    boxes_per_panel <- max(panel_label_counts)
  }

  label_df$panel_span <- pmax(label_df$panel_max - label_df$panel_min, 0)
  label_df$label_nudge <- pmax(label_df$panel_span * 0.03, pmax(abs(label_df$median_value), 1) * 0.01)
  label_df$label_y <- label_df$median_value + label_df$label_nudge
  label_df$label <- if (is.null(formatter)) as.character(label_df$median_value) else formatter(label_df$median_value)

  enabled <- nrow(label_df) > 0 &&
    boxes_per_panel <= max_boxes_per_panel &&
    panel_count <= max_panels &&
    nrow(label_df) <= max_labels

  list(
    enabled = enabled,
    data = label_df,
    upper_expand = if (enabled) 0.14 else 0.06
  )
}

add_box_median_labels <- function(plot_obj, annotation, x, fill = NULL, dodge_width = NULL, size = 3.8) {
  if (!annotation$enabled) return(plot_obj)
  mapping <- aes(x = .data[[x]], y = label_y, label = label)
  position <- position_identity()
  if (!is.null(fill) && !is.null(dodge_width)) {
    mapping <- aes(x = .data[[x]], y = label_y, label = label, group = .data[[fill]])
    position <- position_dodge(width = dodge_width)
  }
  plot_obj +
    geom_text(
      data = annotation$data,
      mapping = mapping,
      inherit.aes = FALSE,
      position = position,
      vjust = 0,
      size = size,
      color = colors[["carbon"]],
      check_overlap = TRUE,
      show.legend = FALSE
    )
}

box_jitter <- function(df, x, y, fill = NULL, title = NULL, subtitle = NULL, ylab = NULL, facet_cols = NULL) {
  if (nrow(df) == 0) return(no_data("No data for this comparison."))
  annotation <- build_box_median_annotation(
    df,
    x,
    y,
    fill = fill,
    facet_cols = facet_cols,
    formatter = function(values) format_box_median_labels(values, y, ylab)
  )
  mapping <- if (is.null(fill)) {
    aes(x = .data[[x]], y = .data[[y]])
  } else {
    aes(x = .data[[x]], y = .data[[y]], fill = .data[[fill]])
  }
  p <- ggplot(df, mapping) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.6) +
    labs(title = title, subtitle = subtitle, x = NULL, y = ylab, fill = NULL) +
    base_plot_theme()
  p <- add_box_median_labels(p, annotation, x)
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, annotation$upper_expand)))
}

delta_table <- function(table_name, metric_expr, benchmark_select_expr, benchmark_group_cols, benchmark_output_cols,
                        lower_is_better = FALSE, where_clause = "1 = 1") {
  direction_expr <- if (lower_is_better) "-1" else "1"
  group_cols <- paste(c("placement_class", "client_machine_type", "server_machine_type", "protocol", benchmark_group_cols, "os_tuning"), collapse = ", ")
  join_cols <- c("placement_class", "client_machine_type", "server_machine_type", "protocol", benchmark_group_cols)
  join_condition <- paste(sprintf("s.%s is not distinct from t.%s", join_cols, join_cols), collapse = "\n        and ")
  paired_select_cols <- paste(paste0("s.", c("placement_class", "client_machine_type", "protocol", benchmark_output_cols)), collapse = ", ")
  output_cols <- paste(c("placement_class", "client_machine_type", "protocol", benchmark_output_cols), collapse = ", ")
  order_cols <- paste(c("placement_class", "client_machine_type", "protocol", benchmark_output_cols), collapse = ", ")
  sql(glue::glue("
    with base as (
      select placement_class, client_machine_type, server_machine_type, protocol,
             {benchmark_select_expr},
             os_tuning, {metric_expr} as metric
      from {table_name}
      where {where_clause}
    ),
    agg as (
      select {group_cols},
             median(metric) as median_metric, count(*) as n
      from base
      where metric is not null
      group by {group_cols}
    ),
    paired as (
      select {paired_select_cols},
             s.median_metric as standard_median,
             t.median_metric as tuned_median,
             s.n as standard_n,
             t.n as tuned_n,
             ((t.median_metric - s.median_metric) / nullif(s.median_metric, 0)) * 100 as raw_delta_pct
      from agg s
      join agg t
        on {join_condition}
      where s.os_tuning = 'standard' and t.os_tuning = 'tuned'
    )
    select {output_cols},
           round(standard_median, 3) as standard_median,
           round(tuned_median, 3) as tuned_median,
           standard_n, tuned_n,
           round(raw_delta_pct, 2) as delta_pct,
           round(raw_delta_pct * {direction_expr}, 2) as improvement_pct
    from paired
    order by {order_cols}
  "))
}
```

```{r data-availability, include=FALSE}
counts <- sql("
select
  (select count(*) from scenarios) as scenarios,
  (select count(*) from iperf3) as iperf3_repetitions,
  (select count(*) from sockperf) as sockperf_repetitions,
  (select count(*) from iperf3_intervals) as iperf3_intervals,
  (select count(distinct run_id) from scenarios) as runs
")
```

This report analyzes network benchmark results from `r result_id`.

```{r note, results='asis', echo=FALSE}
if (!is.null(params$note) && nzchar(params$note)) {
  cat(sprintf("> %s\n\n", params$note))
}
```

# Data Coverage

The main analysis uses one row per benchmark repetition. iperf3 interval rows are kept for diagnostics only and are not treated as independent benchmark repetitions.

```{r filter-policy, echo=FALSE}
filter_policy <- data.frame(
  section = c(
    "TCP throughput",
    "UDP throughput",
    "UDP packet-size impact",
    "Latency placement impact",
    "Latency instance impact",
    "Latency message-size impact"
  ),
  default_filter = c(
    sprintf("protocol = tcp; tcp_length_bytes = %s; stream count and OS tuning are separated by facets where relevant", ref_tcp_length_bytes),
    sprintf("protocol = udp; broad comparisons use udp_length_bytes = %s; UDP target rate and stream count are fixed or shown explicitly", ref_udp_length_bytes),
    sprintf("protocol = udp; client_machine_type = %s; udp_target_bitrate_gbit_per_sec = %s; packet size is shown on the x-axis", large_machine, ref_udp_target_gbps),
    sprintf("sockperf; comparable placement pairs only; os_tuning is split into standard/tuned subsections; message sizes are limited to %s B and 8192 B", ref_msg_size_bytes),
    sprintf("sockperf; placement_class = %s; msg_size_bytes = %s; protocol and OS tuning are separated by facets", ref_placement, ref_msg_size_bytes),
    sprintf("sockperf; client_machine_type = %s; os_tuning = %s; message size is shown on the x-axis", large_machine, ref_os_tuning)
  )
)
kable(filter_policy, caption = "Default filters used to keep network comparisons comparable")
```

```{r coverage-counts}
kable(counts, caption = "Parsed network benchmark data")
```

```{r scenario-matrix}
scenario_matrix <- sql("
select run_id, scenario_name, placement_class, client_machine_type,
       client_availability_zone, server_availability_zone, os_tuning,
       count(*) over (partition by run_id, scenario_name) as scenario_rows
from scenarios
order by run_id, scenario_name
")
kable(scenario_matrix, caption = "Scenario coverage")
```

```{r benchmark-coverage}
benchmark_coverage <- sql("
select 'iperf3' as tool, protocol, benchmark_name, count(*) as repetitions
from iperf3
group by 1, 2, 3
union all
select 'sockperf' as tool, protocol, benchmark_name, count(*) as repetitions
from sockperf
group by 1, 2, 3
order by tool, protocol, benchmark_name
")
kable(benchmark_coverage, caption = "Benchmark repetition coverage")
```

# Throughput

```{r throughput-intro, results='asis'}
cat(sprintf(
"Throughput plots use `network_iperf3.csv`, one row per iperf3 repetition. The primary metric is receiver throughput in Mbit/s. Broad TCP comparisons fix `tcp_length_bytes = %s`. Broad UDP comparisons fix `udp_length_bytes = %s`; the dedicated packet-size section compares the packet sizes actually present. UDP throughput must be interpreted together with loss and jitter.\n",
  ref_tcp_length_bytes, ref_udp_length_bytes
))
```

## Placement Impact

Two placement comparisons, on the instance types named by
`placement_comparison_small_machine` and `placement_comparison_large_machine`:

```{r placement-intro, results='asis'}
cat(sprintf("- `%s`: co-located single-AZ vs different-host single-AZ.\n", small_machine))
cat(sprintf("- `%s`: different-host single-AZ vs multi-AZ.\n", large_machine))
```

```{r tcp-placement-small, fig.width=13, fig.height=6.5}
tcp_place_small <- sql(sprintf("
select placement_class, os_tuning, parallel_streams,
       receiver_mbit_per_sec
from iperf3
where protocol = 'tcp'
  and tcp_length_bytes = %s
  and client_machine_type = %s
  and placement_class in ('co-located-single-az', 'different-host-single-az')
", ref_tcp_length_bytes, q_small))
if (nrow(tcp_place_small) == 0) {
  no_data(sprintf("No comparable %s TCP placement data.", small_machine))
} else {
  tcp_place_small$placement_class <- format_placement(tcp_place_small$placement_class)
  tcp_place_small$stream_label <- paste0(tcp_place_small$parallel_streams, " stream(s)")
  box_jitter(
    tcp_place_small, "placement_class", "receiver_mbit_per_sec", "placement_class",
    sprintf("TCP throughput: co-located vs different-host (%s)", small_machine),
    sprintf("Fixed tcp_length_bytes = %s; facets keep stream count and OS tuning separate.", ref_tcp_length_bytes),
    "Receiver throughput (Mbit/s)",
    facet_cols = c("os_tuning", "stream_label")
  ) +
    facet_grid(os_tuning ~ stream_label) +
    guides(fill = "none")
}
```

```{r tcp-placement-large, fig.width=13, fig.height=6.5}
tcp_place_large <- sql(sprintf("
select placement_class, os_tuning, parallel_streams,
       receiver_mbit_per_sec
from iperf3
where protocol = 'tcp'
  and tcp_length_bytes = %s
  and client_machine_type = %s
  and placement_class in ('different-host-single-az', 'multi-az')
", ref_tcp_length_bytes, q_large))
if (nrow(tcp_place_large) == 0) {
  no_data(sprintf("No comparable %s TCP placement data.", large_machine))
} else {
  tcp_place_large$placement_class <- format_placement(tcp_place_large$placement_class)
  tcp_place_large$stream_label <- paste0(tcp_place_large$parallel_streams, " stream(s)")
  box_jitter(
    tcp_place_large, "placement_class", "receiver_mbit_per_sec", "placement_class",
    sprintf("TCP throughput: single-AZ vs multi-AZ (%s)", large_machine),
    sprintf("Fixed tcp_length_bytes = %s; facets keep stream count and OS tuning separate.", ref_tcp_length_bytes),
    "Receiver throughput (Mbit/s)",
    facet_cols = c("os_tuning", "stream_label")
  ) +
    facet_grid(os_tuning ~ stream_label) +
    guides(fill = "none")
}
```

```{r udp-placement-summary}
udp_placement_summary <- sql(sprintf("
select placement_class, client_machine_type, os_tuning,
       udp_target_bitrate_gbit_per_sec as target_gbps,
       udp_length_bytes, parallel_streams,
       count(*) as n,
       round(median(receiver_mbit_per_sec), 1) as median_recv_mbps,
       round(median(lost_percent), 2) as median_loss_pct,
       round(median(jitter_ms), 4) as median_jitter_ms
from iperf3
where protocol = 'udp'
  and udp_length_bytes = %s
group by 1, 2, 3, 4, 5, 6
order by placement_class, client_machine_type, os_tuning, target_gbps, udp_length_bytes, parallel_streams
", ref_udp_length_bytes))
kable(udp_placement_summary, caption = sprintf("UDP throughput, loss, and jitter by placement and benchmark parameters; fixed udp_length_bytes = %s", ref_udp_length_bytes))
```

## Instance Type Impact

```{r instance-intro, results='asis'}
cat(sprintf(
  "Instance type comparisons fix placement to `%s` to avoid mixing unrelated placement classes. Instance types are whatever the result set contains.\n",
  ref_placement
))
```

```{r tcp-instance-impact, fig.width=13, fig.height=6.5}
tcp_instance <- sql(sprintf("
select placement_class, client_machine_type, os_tuning, parallel_streams,
       receiver_mbit_per_sec
from iperf3
where protocol = 'tcp'
  and tcp_length_bytes = %s
  and placement_class = %s
", ref_tcp_length_bytes, q_placement))
if (nrow(tcp_instance) == 0) {
  no_data("No comparable TCP instance type data.")
} else {
  tcp_instance$placement_class <- format_placement(tcp_instance$placement_class)
  tcp_instance$stream_label <- paste0(tcp_instance$parallel_streams, " stream(s)")
  tcp_instance_annotation <- build_box_median_annotation(
    tcp_instance,
    "client_machine_type",
    "receiver_mbit_per_sec",
    fill = "client_machine_type",
    facet_cols = c("os_tuning", "stream_label"),
    formatter = function(values) format_box_median_labels(values, "receiver_mbit_per_sec", "Receiver throughput (Mbit/s)")
  )
  p <- ggplot(tcp_instance, aes(x = client_machine_type, y = receiver_mbit_per_sec, fill = client_machine_type)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.6) +
    facet_grid(os_tuning ~ stream_label) +
    labs(
      title = "TCP throughput by instance type",
      subtitle = sprintf("Filtered to %s and tcp_length_bytes = %s.", ref_placement, ref_tcp_length_bytes),
      x = NULL, y = "Receiver throughput (Mbit/s)", fill = "Instance type"
    ) +
    base_plot_theme()
  p <- add_box_median_labels(p, tcp_instance_annotation, "client_machine_type")
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, tcp_instance_annotation$upper_expand)))
}
```

```{r udp-instance-impact, fig.width=13, fig.height=6.5}
udp_instance <- sql(sprintf("
select placement_class, client_machine_type, os_tuning, parallel_streams,
       receiver_mbit_per_sec, lost_percent
from iperf3
where protocol = 'udp'
  and udp_length_bytes = %s
  and placement_class = %s
  and udp_target_bitrate_gbit_per_sec = %s
", ref_udp_length_bytes, q_placement, ref_udp_target_gbps))
if (nrow(udp_instance) == 0) {
  no_data("No comparable UDP instance type data.")
} else {
  udp_instance$placement_class <- format_placement(udp_instance$placement_class)
  udp_instance$stream_label <- paste0(udp_instance$parallel_streams, " stream(s)")
  udp_instance_annotation <- build_box_median_annotation(
    udp_instance,
    "client_machine_type",
    "receiver_mbit_per_sec",
    fill = "client_machine_type",
    facet_cols = c("os_tuning", "stream_label"),
    formatter = function(values) format_box_median_labels(values, "receiver_mbit_per_sec", "Receiver throughput (Mbit/s)")
  )
  p <- ggplot(udp_instance, aes(x = client_machine_type, y = receiver_mbit_per_sec, fill = client_machine_type)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.6) +
    facet_grid(os_tuning ~ stream_label) +
    labs(
      title = "UDP throughput by instance type",
      subtitle = sprintf("Filtered to %s, udp_target_bitrate_gbit_per_sec = %s, and udp_length_bytes = %s.", ref_placement, ref_udp_target_gbps, ref_udp_length_bytes),
      x = NULL, y = "Receiver throughput (Mbit/s)", fill = "Instance type"
    ) +
    base_plot_theme()
  p <- add_box_median_labels(p, udp_instance_annotation, "client_machine_type")
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, udp_instance_annotation$upper_expand)))
}
```

## OS Tuning Impact

The OS tuning table pairs standard and tuned measurements only when placement, instance type, protocol, and explicit benchmark parameters match.

```{r throughput-tuning-table}
throughput_tuning <- delta_table(
  "iperf3",
  "receiver_mbit_per_sec",
  "parallel_streams,
   tcp_length_bytes,
   udp_length_bytes,
   udp_target_bitrate_gbit_per_sec as udp_target_gbit_per_sec",
  c("parallel_streams", "tcp_length_bytes", "udp_length_bytes", "udp_target_gbit_per_sec"),
  c("parallel_streams", "tcp_length_bytes", "udp_length_bytes", "udp_target_gbit_per_sec"),
  lower_is_better = FALSE,
  where_clause = sprintf("receiver_mbit_per_sec is not null
                  and ((protocol = 'tcp' and tcp_length_bytes = %s)
                       or (protocol = 'udp' and udp_length_bytes = %s))",
                         ref_tcp_length_bytes, ref_udp_length_bytes)
)
kable(throughput_tuning, caption = "OS tuning impact on iperf3 receiver throughput; paired by explicit benchmark parameter columns")
```

## Protocol And UDP-Specific Effects

TCP and UDP have different benchmark semantics, so this section emphasizes protocol-specific behavior rather than treating them as equivalent.

```{r tcp-stream-impact, fig.width=12, fig.height=6}
tcp_stream <- sql(sprintf("
select placement_class, client_machine_type, os_tuning, parallel_streams,
       receiver_mbit_per_sec
from iperf3
where protocol = 'tcp'
  and tcp_length_bytes = %s
  and client_machine_type = %s
", ref_tcp_length_bytes, q_large))
if (nrow(tcp_stream) == 0) {
  no_data("No TCP data.")
} else {
  tcp_stream$placement_class <- format_placement(tcp_stream$placement_class)
  tcp_stream$stream_label <- paste0(tcp_stream$parallel_streams, " stream(s)")
  tcp_stream_annotation <- build_box_median_annotation(
    tcp_stream,
    "stream_label",
    "receiver_mbit_per_sec",
    fill = "stream_label",
    facet_cols = c("placement_class", "os_tuning"),
    formatter = function(values) format_box_median_labels(values, "receiver_mbit_per_sec", "Receiver throughput (Mbit/s)")
  )
  p <- ggplot(tcp_stream, aes(x = stream_label, y = receiver_mbit_per_sec, fill = stream_label)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(placement_class ~ os_tuning) +
    labs(
      title = "TCP stream count impact",
      subtitle = sprintf("Filtered to client_machine_type = '%s' and tcp_length_bytes = %s; placement and OS tuning are separated by facets.", large_machine, ref_tcp_length_bytes),
      x = NULL, y = "Receiver throughput (Mbit/s)", fill = NULL
    ) +
    base_plot_theme()
  p <- add_box_median_labels(p, tcp_stream_annotation, "stream_label")
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, tcp_stream_annotation$upper_expand)))
}
```

```{r udp-throughput-loss, fig.width=14, fig.height=7}
udp_loss <- sql(sprintf("
select placement_class, client_machine_type, os_tuning,
       concat(cast(udp_target_bitrate_gbit_per_sec as varchar), ' Gbit/s, ',
              cast(parallel_streams as varchar), ' stream(s)') as udp_case,
       receiver_mbit_per_sec, lost_percent
from iperf3
where protocol = 'udp'
  and udp_length_bytes = %s
  and client_machine_type = %s
", ref_udp_length_bytes, q_large))
if (nrow(udp_loss) == 0) {
  no_data("No UDP data.")
} else {
  udp_loss$placement_class <- format_placement(udp_loss$placement_class)
  udp_loss_annotation <- build_box_median_annotation(
    udp_loss,
    "udp_case",
    "lost_percent",
    fill = "placement_class",
    facet_cols = c("placement_class", "os_tuning"),
    formatter = function(values) format_box_median_labels(values, "lost_percent", "Lost packets (%)")
  )
  p <- ggplot(udp_loss, aes(x = udp_case, y = lost_percent, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(placement_class ~ os_tuning, scales = "free_x", space = "free_x") +
    labs(
      title = "UDP packet loss by target rate",
      subtitle = sprintf("Filtered to client_machine_type = '%s' and udp_length_bytes = %s; packet-size effects are shown separately.", large_machine, ref_udp_length_bytes),
      x = NULL, y = "Lost packets (%)", fill = "Placement"
    ) +
    base_plot_theme() +
    theme(axis.text.x = element_text(angle = 35, hjust = 1), legend.position = "none")
  p <- add_box_median_labels(p, udp_loss_annotation, "udp_case")
  p + scale_y_continuous(labels = label_percent(scale = 1), limits = c(0, NA), expand = expansion(mult = c(0, udp_loss_annotation$upper_expand)))
}
```

```{r udp-jitter-table}
udp_jitter <- sql(sprintf("
select placement_class, client_machine_type, os_tuning,
       udp_target_bitrate_gbit_per_sec as target_gbps,
       udp_length_bytes, parallel_streams,
       count(*) as n,
       round(median(jitter_ms), 4) as median_jitter_ms,
       round(max(jitter_ms), 4) as max_jitter_ms
from iperf3
where protocol = 'udp'
  and udp_length_bytes = %s
  and client_machine_type = %s
group by 1, 2, 3, 4, 5, 6
order by placement_class, client_machine_type, os_tuning, target_gbps, udp_length_bytes, parallel_streams
", ref_udp_length_bytes, q_large))
kable(udp_jitter, caption = sprintf("UDP jitter summary; filtered to client_machine_type = '%s' and fixed udp_length_bytes = %s", large_machine, ref_udp_length_bytes))
```

## Packet And Message Size Impact

The broad throughput comparisons above keep packet/message size fixed. This section isolates the available size dimensions.

```{r tcp-size-summary}
tcp_size_summary <- sql("
select tcp_length_bytes, count(*) as n,
       round(median(receiver_mbit_per_sec), 1) as median_recv_mbps,
       round(min(receiver_mbit_per_sec), 1) as min_recv_mbps,
       round(max(receiver_mbit_per_sec), 1) as max_recv_mbps
from iperf3
where protocol = 'tcp'
group by 1
order by 1
")
kable(tcp_size_summary, caption = "TCP payload-size coverage. Current data has only one TCP length, so there is no TCP size comparison yet.")
```

```{r udp-packet-size-impact, fig.width=13, fig.height=8.5}
udp_size <- sql(sprintf("
select placement_class, client_machine_type, os_tuning, parallel_streams,
       udp_length_bytes, receiver_mbit_per_sec, lost_percent
from iperf3
where protocol = 'udp'
  and udp_target_bitrate_gbit_per_sec = %s
  and client_machine_type = %s
", ref_udp_target_gbps, q_large))
if (nrow(udp_size) == 0 || length(unique(udp_size$udp_length_bytes)) < 2) {
  no_data("No comparable UDP packet-size data with at least two packet sizes.")
} else {
  udp_size$placement_class <- format_placement(udp_size$placement_class)
  udp_size$size_label <- paste0(udp_size$udp_length_bytes, " B")
  udp_size$stream_label <- paste0(udp_size$parallel_streams, " stream(s)")
  udp_size_throughput_annotation <- build_box_median_annotation(
    udp_size,
    "size_label",
    "receiver_mbit_per_sec",
    fill = "size_label",
    facet_cols = c("placement_class", "os_tuning", "stream_label"),
    formatter = function(values) format_box_median_labels(values, "receiver_mbit_per_sec", "Receiver throughput (Mbit/s)")
  )
  p <- ggplot(udp_size, aes(x = size_label, y = receiver_mbit_per_sec, fill = size_label)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(placement_class + os_tuning ~ stream_label) +
    labs(
      title = "UDP throughput by packet size",
      subtitle = sprintf("Filtered to %s and %s Gbit/s target rate; placement, tuning, and stream count are separated.", large_machine, ref_udp_target_gbps),
      x = "UDP packet size", y = "Receiver throughput (Mbit/s)", fill = "Packet size"
    ) +
    base_plot_theme()
  p <- add_box_median_labels(p, udp_size_throughput_annotation, "size_label")
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, udp_size_throughput_annotation$upper_expand)))
}
```

```{r udp-packet-size-loss, fig.width=13, fig.height=8.5}
if (nrow(udp_size) == 0 || length(unique(udp_size$udp_length_bytes)) < 2) {
  no_data("No comparable UDP packet-size data with at least two packet sizes.")
} else {
  udp_size_loss_annotation <- build_box_median_annotation(
    udp_size,
    "size_label",
    "lost_percent",
    fill = "size_label",
    facet_cols = c("placement_class", "os_tuning", "stream_label"),
    formatter = function(values) format_box_median_labels(values, "lost_percent", "Lost packets (%)")
  )
  p <- ggplot(udp_size, aes(x = size_label, y = lost_percent, fill = size_label)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(placement_class + os_tuning ~ stream_label) +
    labs(
      title = "UDP packet loss by packet size",
      subtitle = "Same filtered subset as the packet-size throughput plot.",
      x = "UDP packet size", y = "Lost packets (%)", fill = "Packet size"
    ) +
    base_plot_theme()
  p <- add_box_median_labels(p, udp_size_loss_annotation, "size_label")
  p + scale_y_continuous(labels = label_percent(scale = 1), limits = c(0, NA), expand = expansion(mult = c(0, udp_size_loss_annotation$upper_expand)))
}
```

# Latency

Latency plots use `network_sockperf.csv`, one row per sockperf repetition. The report includes average latency and tail percentiles. Tail latency values are summary percentiles emitted by sockperf per repetition, not raw per-message samples.

## Placement Impact

As with throughput, placement comparisons use comparable subsets.

### Standard OS Tuning

```{r latency-placement-g2a2d-standard, fig.width=14, fig.height=8}
lat_place_2d_standard <- sql(sprintf("
with base as (
  select placement_class, os_tuning, protocol, msg_size_bytes,
         avg_rtt_us, p50_rtt_us, p99_rtt_us, p999_rtt_us
  from sockperf
  where client_machine_type = %s
    and placement_class in ('co-located-single-az', 'different-host-single-az')
    and msg_size_bytes in (64, 8192)
    and os_tuning = 'standard'
)
select placement_class, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
", q_small))
if (nrow(lat_place_2d_standard) == 0) {
  no_data(sprintf("No comparable %s latency placement data for standard OS tuning.", small_machine))
} else {
  lat_place_2d_standard$placement_class <- format_placement(lat_place_2d_standard$placement_class)
  lat_place_2d_standard$metric <- factor(lat_place_2d_standard$metric, levels = c("avg", "p50", "p99", "p99.9"))
  lat_place_2d_standard$msg_label <- paste0(lat_place_2d_standard$protocol, " / ", lat_place_2d_standard$msg_size_bytes, " B")
  lat_place_2d_standard_annotation <- build_box_median_annotation(
    lat_place_2d_standard,
    "placement_class",
    "latency_us",
    fill = "placement_class",
    facet_cols = c("metric", "msg_label"),
    formatter = function(values) format_box_median_labels(values, "latency_us", "RTT (us)")
  )
  p <- ggplot(lat_place_2d_standard, aes(x = placement_class, y = latency_us, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.3) +
    facet_grid(metric ~ msg_label, scales = "free_y") +
    labs(
      title = sprintf("Latency: co-located vs different-host (%s)", small_machine),
      subtitle = "Filtered to os_tuning = 'standard'; message sizes limited to 64 B and 8192 B.",
      x = NULL, y = "RTT (us)", fill = NULL
    ) +
    base_plot_theme() +
    guides(fill = "none")
  p <- add_box_median_labels(p, lat_place_2d_standard_annotation, "placement_class")
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, lat_place_2d_standard_annotation$upper_expand)))
}
```

```{r latency-placement-g2a120d-standard, fig.width=14, fig.height=8}
lat_place_120d_standard <- sql(sprintf("
with base as (
  select placement_class, os_tuning, protocol, msg_size_bytes,
         avg_rtt_us, p50_rtt_us, p99_rtt_us, p999_rtt_us
  from sockperf
  where client_machine_type = %s
    and placement_class in ('different-host-single-az', 'multi-az')
    and msg_size_bytes in (64, 8192)
    and os_tuning = 'standard'
)
select placement_class, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
", q_large))
if (nrow(lat_place_120d_standard) == 0) {
  no_data(sprintf("No comparable %s latency placement data for standard OS tuning.", large_machine))
} else {
  lat_place_120d_standard$placement_class <- format_placement(lat_place_120d_standard$placement_class)
  lat_place_120d_standard$metric <- factor(lat_place_120d_standard$metric, levels = c("avg", "p50", "p99", "p99.9"))
  lat_place_120d_standard$msg_label <- paste0(lat_place_120d_standard$protocol, " / ", lat_place_120d_standard$msg_size_bytes, " B")
  lat_place_120d_standard_annotation <- build_box_median_annotation(
    lat_place_120d_standard,
    "placement_class",
    "latency_us",
    fill = "placement_class",
    facet_cols = c("metric", "msg_label"),
    formatter = function(values) format_box_median_labels(values, "latency_us", "RTT (us)")
  )
  p <- ggplot(lat_place_120d_standard, aes(x = placement_class, y = latency_us, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.3) +
    facet_grid(metric ~ msg_label, scales = "free_y") +
    labs(
      title = sprintf("Latency: single-AZ vs multi-AZ (%s)", large_machine),
      subtitle = "Filtered to os_tuning = 'standard'; message sizes limited to 64 B and 8192 B.",
      x = NULL, y = "RTT (us)", fill = NULL
    ) +
    base_plot_theme() +
    guides(fill = "none")
  p <- add_box_median_labels(p, lat_place_120d_standard_annotation, "placement_class")
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, lat_place_120d_standard_annotation$upper_expand)))
}
```

### Tuned OS Tuning

```{r latency-placement-g2a2d-tuned, fig.width=14, fig.height=8}
lat_place_2d_tuned <- sql(sprintf("
with base as (
  select placement_class, os_tuning, protocol, msg_size_bytes,
         avg_rtt_us, p50_rtt_us, p99_rtt_us, p999_rtt_us
  from sockperf
  where client_machine_type = %s
    and placement_class in ('co-located-single-az', 'different-host-single-az')
    and msg_size_bytes in (64, 8192)
    and os_tuning = 'tuned'
)
select placement_class, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
", q_small))
if (nrow(lat_place_2d_tuned) == 0) {
  no_data(sprintf("No comparable %s latency placement data for tuned OS tuning.", small_machine))
} else {
  lat_place_2d_tuned$placement_class <- format_placement(lat_place_2d_tuned$placement_class)
  lat_place_2d_tuned$metric <- factor(lat_place_2d_tuned$metric, levels = c("avg", "p50", "p99", "p99.9"))
  lat_place_2d_tuned$msg_label <- paste0(lat_place_2d_tuned$protocol, " / ", lat_place_2d_tuned$msg_size_bytes, " B")
  lat_place_2d_tuned_annotation <- build_box_median_annotation(
    lat_place_2d_tuned,
    "placement_class",
    "latency_us",
    fill = "placement_class",
    facet_cols = c("metric", "msg_label"),
    formatter = function(values) format_box_median_labels(values, "latency_us", "RTT (us)")
  )
  p <- ggplot(lat_place_2d_tuned, aes(x = placement_class, y = latency_us, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.3) +
    facet_grid(metric ~ msg_label, scales = "free_y") +
    labs(
      title = sprintf("Latency: co-located vs different-host (%s)", small_machine),
      subtitle = "Filtered to os_tuning = 'tuned'; message sizes limited to 64 B and 8192 B.",
      x = NULL, y = "RTT (us)", fill = NULL
    ) +
    base_plot_theme() +
    guides(fill = "none")
  p <- add_box_median_labels(p, lat_place_2d_tuned_annotation, "placement_class")
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, lat_place_2d_tuned_annotation$upper_expand)))
}
```

```{r latency-placement-g2a120d-tuned, fig.width=14, fig.height=8}
lat_place_120d_tuned <- sql(sprintf("
with base as (
  select placement_class, os_tuning, protocol, msg_size_bytes,
         avg_rtt_us, p50_rtt_us, p99_rtt_us, p999_rtt_us
  from sockperf
  where client_machine_type = %s
    and placement_class in ('different-host-single-az', 'multi-az')
    and msg_size_bytes in (64, 8192)
    and os_tuning = 'tuned'
)
select placement_class, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
", q_large))
if (nrow(lat_place_120d_tuned) == 0) {
  no_data(sprintf("No comparable %s latency placement data for tuned OS tuning.", large_machine))
} else {
  lat_place_120d_tuned$placement_class <- format_placement(lat_place_120d_tuned$placement_class)
  lat_place_120d_tuned$metric <- factor(lat_place_120d_tuned$metric, levels = c("avg", "p50", "p99", "p99.9"))
  lat_place_120d_tuned$msg_label <- paste0(lat_place_120d_tuned$protocol, " / ", lat_place_120d_tuned$msg_size_bytes, " B")
  lat_place_120d_tuned_annotation <- build_box_median_annotation(
    lat_place_120d_tuned,
    "placement_class",
    "latency_us",
    fill = "placement_class",
    facet_cols = c("metric", "msg_label"),
    formatter = function(values) format_box_median_labels(values, "latency_us", "RTT (us)")
  )
  p <- ggplot(lat_place_120d_tuned, aes(x = placement_class, y = latency_us, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.3) +
    facet_grid(metric ~ msg_label, scales = "free_y") +
    labs(
      title = sprintf("Latency: single-AZ vs multi-AZ (%s)", large_machine),
      subtitle = "Filtered to os_tuning = 'tuned'; message sizes limited to 64 B and 8192 B.",
      x = NULL, y = "RTT (us)", fill = NULL
    ) +
    base_plot_theme() +
    guides(fill = "none")
  p <- add_box_median_labels(p, lat_place_120d_tuned_annotation, "placement_class")
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, lat_place_120d_tuned_annotation$upper_expand)))
}
```

## Instance Type Impact

```{r latency-instance-impact, fig.width=14, fig.height=8.5}
lat_instance <- sql(sprintf("
select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes,
       avg_rtt_us, p50_rtt_us, p99_rtt_us
from sockperf
where placement_class = %s
  and msg_size_bytes = %s
", q_placement, ref_msg_size_bytes))
if (nrow(lat_instance) == 0) {
  no_data("No comparable latency instance type data.")
} else {
  lat_instance$placement_class <- format_placement(lat_instance$placement_class)
  lat_instance_long <- sql(sprintf("
    with base as (
      select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes,
             avg_rtt_us, p50_rtt_us, p99_rtt_us
      from sockperf
      where placement_class = %s
        and msg_size_bytes = %s
    )
    select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
    union all
    select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
    union all
    select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
  ", q_placement, ref_msg_size_bytes))
  lat_instance_long$metric <- factor(lat_instance_long$metric, levels = c("avg", "p50", "p99"))
  lat_instance_annotation <- build_box_median_annotation(
    lat_instance_long,
    "client_machine_type",
    "latency_us",
    fill = "client_machine_type",
    facet_cols = c("metric", "protocol", "os_tuning"),
    formatter = function(values) format_box_median_labels(values, "latency_us", "RTT (us)")
  )
  p <- ggplot(lat_instance_long, aes(x = client_machine_type, y = latency_us, fill = client_machine_type)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(metric + protocol ~ os_tuning) +
    labs(
      title = "Latency by instance type",
      subtitle = "Filtered to different-host single-AZ and 64 B messages.",
      x = NULL, y = "RTT (us)", fill = "Instance type"
    ) +
    base_plot_theme()
  p <- add_box_median_labels(p, lat_instance_annotation, "client_machine_type")
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, lat_instance_annotation$upper_expand)))
}
```

## OS Tuning Impact

```{r latency-tuning-table}
latency_tuning <- delta_table(
  "sockperf",
  "p99_rtt_us",
  "msg_size_bytes",
  c("msg_size_bytes"),
  c("msg_size_bytes"),
  lower_is_better = TRUE,
  where_clause = "p99_rtt_us is not null"
)
kable(latency_tuning, caption = "OS tuning impact on sockperf p99 latency; paired by msg_size_bytes; positive improvement means tuned is lower")
```

## Protocol And Message Size Impact

```{r latency-message-size, fig.width=14, fig.height=7}
lat_msg <- sql(sprintf("
select placement_class, os_tuning, protocol, msg_size_bytes,
       p50_rtt_us, p99_rtt_us, p999_rtt_us
from sockperf
where os_tuning = %s
  and client_machine_type = %s
", q_tuning, q_large))
if (nrow(lat_msg) == 0) {
  no_data(sprintf("No sockperf data for os_tuning = '%s' and client_machine_type = '%s'.", ref_os_tuning, large_machine))
} else {
  lat_msg_long <- sql(sprintf("
    with base as (
      select placement_class, os_tuning, protocol, msg_size_bytes,
             p50_rtt_us, p99_rtt_us, p999_rtt_us
      from sockperf
      where os_tuning = %s
        and client_machine_type = %s
    )
    select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
    union all
    select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
    union all
    select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
  ", q_tuning, q_large))
  lat_msg_long$placement_class <- format_placement(lat_msg_long$placement_class)
  lat_msg_long$metric <- factor(lat_msg_long$metric, levels = c("p50", "p99", "p99.9"))
  lat_msg_long$msg_size_label <- factor(lat_msg_long$msg_size_bytes)
  lat_msg_annotation <- build_box_median_annotation(
    lat_msg_long,
    "msg_size_label",
    "latency_us",
    fill = "protocol",
    facet_cols = c("metric", "placement_class"),
    formatter = function(values) format_box_median_labels(values, "latency_us", "RTT (us)")
  )
  p <- ggplot(lat_msg_long, aes(x = msg_size_label, y = latency_us, fill = protocol)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7, position = position_dodge(width = 0.75)) +
    facet_grid(metric ~ placement_class, scales = "free_y") +
    labs(
      title = "Latency by message size and protocol",
      subtitle = sprintf("Filtered to os_tuning = '%s' and client_machine_type = '%s'; placement is separated by facets.", ref_os_tuning, large_machine),
      x = "Message size (bytes)", y = "RTT (us)", fill = "Protocol"
    ) +
    base_plot_theme()
  p <- add_box_median_labels(p, lat_msg_annotation, "msg_size_label", fill = "protocol", dodge_width = 0.75)
  p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, lat_msg_annotation$upper_expand)))
}
```

# Diagnostics

This section uses interval-level iperf3 data to inspect run stability. It should not be used as the primary statistical sample for throughput comparisons.

```{r interval-diagnostics, fig.width=14, fig.height=7}
interval_diag <- sql("
select run_id, scenario_name, placement_class, os_tuning, benchmark_name, repetition,
       interval_start_sec, mbit_per_sec
from iperf3_intervals
where omitted = false
  and protocol = 'tcp'
  and benchmark_name = 'iperf3-tcp-1s'
")
if (nrow(interval_diag) == 0) {
  no_data("No interval diagnostics data.")
} else {
  interval_diag$placement_class <- format_placement(interval_diag$placement_class)
  ggplot(interval_diag, aes(x = interval_start_sec, y = mbit_per_sec, group = interaction(run_id, scenario_name, repetition), color = placement_class)) +
    geom_line(alpha = 0.35, linewidth = 0.5) +
    facet_grid(placement_class ~ os_tuning) +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
    labs(
      title = "TCP throughput interval diagnostics",
      subtitle = "Each line is one repetition of iperf3-tcp-1s; this is a stability view, not the main aggregate sample.",
      x = "Interval start (s)", y = "Throughput (Mbit/s)", color = "Placement"
    ) +
    base_plot_theme()
}
```

# Appendix: OS Tuning Profile

The `tuned` label in this report corresponds to the `network-throughput` profile applied by `/opt/cloud-measuring/bin/apply-os-tuning.sh` on both benchmark nodes. The `standard` profile leaves the OS network settings unchanged.

```{r tuning-appendix, echo=FALSE}
tuning_parameters <- data.frame(
  category = c(
    "Queue discipline and congestion control",
    "Queue discipline and congestion control",
    "Socket buffer limits",
    "Socket buffer limits",
    "Socket buffer limits",
    "Socket buffer limits",
    "UDP buffer minimums",
    "UDP buffer minimums",
    "Connection backlog and packet processing",
    "Connection backlog and packet processing",
    "Connection backlog and packet processing",
    "Connection backlog and packet processing",
    "TCP/IP behavior",
    "TCP/IP behavior",
    "TCP/IP behavior",
    "Interface-local tuning",
    "Interface-local tuning"
  ),
  setting = c(
    "net.core.default_qdisc",
    "net.ipv4.tcp_congestion_control",
    "net.core.rmem_max",
    "net.core.wmem_max",
    "net.ipv4.tcp_rmem",
    "net.ipv4.tcp_wmem",
    "net.ipv4.udp_rmem_min",
    "net.ipv4.udp_wmem_min",
    "net.core.somaxconn",
    "net.core.netdev_max_backlog",
    "net.core.netdev_budget",
    "net.core.optmem_max",
    "net.ipv4.ip_local_port_range",
    "net.ipv4.tcp_tw_reuse",
    "net.ipv4.tcp_frto",
    "ethtool -G <primary_iface>",
    "ip link set <primary_iface> txqueuelen"
  ),
  tuned_value = c(
    "fq",
    "bbr",
    "134217728",
    "134217728",
    "4096 87380 67108864",
    "4096 65536 67108864",
    "16384",
    "16384",
    "32768",
    "32768",
    "1000",
    "65535",
    "1024 65535",
    "1",
    "0",
    "rx 1024 tx 1024",
    "10000"
  ),
  stringsAsFactors = FALSE
)
kable(tuning_parameters, caption = "Network-throughput OS tuning profile")
```

## Latency vs Offered Rate

Rows from `sockperf` under-load runs (`mode = 'ul'`). Ping-pong rows are excluded
because they have no controlled offered rate: they sit at one message in flight,
which is effectively idle, and at that operating point TCP and UDP move the same
one packet each way. Any protocol difference has to be read off the shape of
these curves rather than from a single point.

```{r latency-rate-delivery}
ul_any <- sql("select count(*) as n from sockperf where mode = 'ul'")
if (ul_any$n == 0) {
  no_data("No under-load (mode = 'ul') sockperf runs in this result set. Run network/benchmarks/latency-vs-rate.")
} else {
  delivery <- sql("
    select scenario_name, placement_class, protocol, offered_mps,
           round(avg(achieved_mps), 0) as achieved_mps,
           round(100.0 * avg(achieved_mps) / nullif(offered_mps, 0), 1) as pct_delivered,
           sum(dropped_messages) as dropped,
           count(*) as n
    from sockperf
    where mode = 'ul' and offered_mps is not null
    group by 1, 2, 3, 4
    order by 1, 3, 4
  ")
  delivery$rung_valid <- ifelse(is.na(delivery$pct_delivered) | delivery$pct_delivered < ul_min_delivered,
                                "NO - offered rate not delivered", "yes")
  kable(delivery, caption = "Offered vs achieved rate. A rung that did not deliver its offered load measures the generator's ceiling, not the network's, and its percentiles describe a load that was never applied.")
}
```

```{r latency-rate-curve, fig.width=14, fig.height=8}
lat_rate <- sql("
select placement_class, provider, protocol, offered_mps, achieved_mps,
       received_messages / nullif(valid_duration_sec, 0) as delivered_mps,
       msg_size_bytes, p50_rtt_us, p99_rtt_us, p999_rtt_us,
       dropped_messages, cpu_idle_pinning_supported, cpu_idle_pinning_requested
from sockperf
where mode = 'ul' and offered_mps is not null
")
if (nrow(lat_rate) == 0) {
  no_data("No under-load sockperf rows to plot.")
} else {
  # Only rungs that actually delivered their offered load are interpretable,
  # measured on arrivals rather than sends -- see the protocol-delta query.
  lat_rate$delivered_pct <- 100 * lat_rate$delivered_mps / lat_rate$offered_mps
  usable <- lat_rate[!is.na(lat_rate$delivered_pct) & lat_rate$delivered_pct >= ul_min_delivered, ]
  dropped_rungs <- nrow(lat_rate) - nrow(usable)

  if (nrow(usable) == 0) {
    no_data(sprintf("No under-load rung delivered at least %g%% of its offered rate.", ul_min_delivered))
  } else {
    long <- rbind(
      data.frame(usable[, c("placement_class", "provider", "protocol", "offered_mps")],
                 percentile = "p50", value = usable$p50_rtt_us, stringsAsFactors = FALSE),
      data.frame(usable[, c("placement_class", "provider", "protocol", "offered_mps")],
                 percentile = "p99", value = usable$p99_rtt_us, stringsAsFactors = FALSE),
      data.frame(usable[, c("placement_class", "provider", "protocol", "offered_mps")],
                 percentile = "p99.9", value = usable$p999_rtt_us, stringsAsFactors = FALSE)
    )
    long$placement_class <- format_placement(long$placement_class)

    p <- ggplot(long, aes(x = offered_mps, y = value, colour = protocol, linetype = percentile)) +
      stat_summary(fun = median, geom = "line", linewidth = 0.9) +
      stat_summary(fun = median, geom = "point", size = 1.8) +
      facet_grid(provider ~ placement_class, scales = "free_y") +
      scale_x_continuous(labels = comma) +
      scale_y_continuous(labels = comma, limits = c(0, NA)) +
      labs(
        title = "Round-trip latency against offered message rate",
        subtitle = sprintf(
          "sockperf under-load, median across repetitions. Rungs delivering <%g%% of offered load excluded (%d of %d).",
          ul_min_delivered, dropped_rungs, nrow(lat_rate)
        ),
        x = "Offered rate (messages/s)", y = "RTT (us)",
        colour = "Protocol", linetype = "Percentile"
      ) +
      base_plot_theme()
    p
  }
}
```

The protocol comparison, which is the study's headline number. Two arms are only
compared when they ran at the same **achieved** load, not merely the same
requested one -- see the note below the table for why that distinction decides
the result.

```{r latency-rate-protocol-delta}
proto_delta <- sql(sprintf("
select placement_class, provider, offered_mps,
       round(median(case when protocol = 'tcp' then achieved_mps end), 0) as tcp_achieved,
       round(median(case when protocol = 'udp' then achieved_mps end), 0) as udp_achieved,
       -- Delivered, not sent. achieved_mps counts messages the generator put on
       -- the wire; a UDP arm can hit any offered rate by dropping the excess,
       -- and on a real run it did -- 100k offered, 100k sent, 92.7k received.
       -- Comparing on sent rate would call that arm load-matched with a TCP arm
       -- carrying 7.3%% more traffic, and attribute the resulting latency
       -- difference to the transport. This is the quantity the two protocols
       -- must actually agree on.
       round(median(case when protocol = 'tcp' then received_messages / nullif(valid_duration_sec, 0) end), 0) as tcp_delivered,
       round(median(case when protocol = 'udp' then received_messages / nullif(valid_duration_sec, 0) end), 0) as udp_delivered,
       round(median(case when protocol = 'tcp' then p50_rtt_us end), 1) as tcp_p50,
       round(median(case when protocol = 'udp' then p50_rtt_us end), 1) as udp_p50,
       round(median(case when protocol = 'tcp' then p99_rtt_us end), 1) as tcp_p99,
       round(median(case when protocol = 'udp' then p99_rtt_us end), 1) as udp_p99
from sockperf
where mode = 'ul' and offered_mps is not null
  -- Admission is on messages that arrived, for the same reason the comparison
  -- is. A percentile computed over a stream that lost 7%% of its messages
  -- describes the survivors, and the lost ones are not a random sample -- they
  -- are disproportionately the ones that would have been slowest. UDP's tail is
  -- therefore flattered by its own loss, which is the opposite of conservative.
  and received_messages / nullif(valid_duration_sec, 0) >= %.4f * offered_mps
group by 1, 2, 3
order by 1, 2, 3
", ul_min_delivered / 100))

if (nrow(proto_delta) == 0) {
  no_data(sprintf(
    "No TCP/UDP under-load rung delivered at least %g%% of its offered rate.",
    ul_min_delivered))
} else {
  # Both arms must exist before a delta means anything.
  both_present <- !is.na(proto_delta$tcp_delivered) & !is.na(proto_delta$udp_delivered)
  mean_delivered <- (proto_delta$tcp_delivered + proto_delta$udp_delivered) / 2
  proto_delta$rate_gap_pct <- ifelse(
    both_present,
    round(100 * abs(proto_delta$tcp_delivered - proto_delta$udp_delivered) /
            pmax(mean_delivered, 1), 1),
    NA_real_)
  # Loss is reported alongside, because a rung can pass the gap test while both
  # arms lose traffic, and a comparison of two degraded arms is not the same
  # claim as a comparison of two healthy ones.
  proto_delta$udp_loss_pct <- ifelse(
    !is.na(proto_delta$udp_achieved) & proto_delta$udp_achieved > 0,
    round(100 * (1 - proto_delta$udp_delivered / proto_delta$udp_achieved), 2),
    NA_real_)

  comparable <- both_present &
    !is.na(proto_delta$rate_gap_pct) &
    proto_delta$rate_gap_pct <= ul_max_rate_gap

  proto_delta$comparable <- ifelse(
    !both_present, "no - one protocol missing",
    ifelse(comparable, "yes", "no - load mismatch"))

  # Suppressed rather than shown-and-caveated: a number in this column is read
  # as the protocol effect, and where the loads differ it is partly a rate
  # effect. There is no honest way to print it and expect the caveat to travel.
  advantage <- function(tcp, udp) ifelse(comparable, round(100 * (tcp - udp) / tcp, 1), NA_real_)
  proto_delta$p50_udp_advantage_pct <- advantage(proto_delta$tcp_p50, proto_delta$udp_p50)
  proto_delta$p99_udp_advantage_pct <- advantage(proto_delta$tcp_p99, proto_delta$udp_p99)

  proto_delta <- proto_delta[, c(
    "placement_class", "provider", "offered_mps",
    "tcp_delivered", "udp_delivered", "rate_gap_pct", "udp_loss_pct",
    "tcp_p50", "udp_p50", "p50_udp_advantage_pct",
    "tcp_p99", "udp_p99", "p99_udp_advantage_pct",
    "comparable")]

  n_bad <- sum(!comparable)
  if (n_bad > 0) {
    cat(sprintf(
      paste0("%d of %d rungs are not comparable and have a blank advantage.\n\n",
             "This is the check that keeps the headline honest, and it compares ",
             "delivered rate rather than sent rate. UDP does not fall behind when ",
             "it is overloaded -- it drops, and keeps sending at the requested ",
             "rate. So a UDP arm reports a healthy achieved rate while carrying ",
             "less traffic end to end than the TCP arm it is being compared with, ",
             "and any latency advantage it then shows is partly the traffic it ",
             "never delivered. Latency against rate is superlinear near the knee, ",
             "so a few percent of load is not a few percent of latency. A rung is ",
             "compared here only when both arms delivered at least %g%% of the ",
             "offered rate and their delivered rates agree within %g%%.\n\n"),
      n_bad, nrow(proto_delta), ul_min_delivered, ul_max_rate_gap))
  }

  kable(proto_delta, caption = sprintf(
    "TCP vs UDP at matched delivered rate. tcp_delivered/udp_delivered are messages that arrived, not messages sent; udp_loss_pct is the gap between the two for UDP. Positive advantage means UDP is lower. Rungs are admitted only if both arms delivered >=%g%% of the offered rate and their delivered rates agree within %g%%; the advantage is blank otherwise. Read down a column: a difference that appears only at higher rungs is the transport cost ping-pong cannot see.",
    ul_min_delivered, ul_max_rate_gap))
}
```

How much data stands behind each percentile. A tail percentile is an order
statistic: p99.9 is estimated from the slowest 0.1% of observations, so at low
offered rates it can rest on a few dozen samples even though the run looks
complete.

```{r latency-rate-tail-support}
tail_support <- sql("
select protocol, offered_mps,
       round(median(coalesce(received_messages, sent_messages)), 0) as rtt_samples_per_rep,
       round(median(reply_every), 0) as reply_every,
       round(median(valid_duration_sec), 1) as valid_sec,
       count(*) as reps
from sockperf
where mode = 'ul' and offered_mps is not null
group by 1, 2
order by 2, 1
")
if (nrow(tail_support) == 0) {
  no_data("No under-load rows to assess percentile support.")
} else {
  # reply_every = 1 means every message is echoed, so replies received is the
  # RTT observation count directly. Sample counts are per repetition because
  # sockperf computes its percentiles per run; pooling reps would overstate the
  # support behind any single reported percentile.
  tail_support$p99_samples <- floor(tail_support$rtt_samples_per_rep * 0.01)
  tail_support$p999_samples <- floor(tail_support$rtt_samples_per_rep * 0.001)
  tail_support$p99_usable <- ifelse(tail_support$p99_samples >= ul_min_tail_samples, "yes", "thin")
  tail_support$p999_usable <- ifelse(tail_support$p999_samples >= ul_min_tail_samples, "yes", "thin")

  thin_999 <- tail_support[tail_support$p999_samples < ul_min_tail_samples, ]
  if (nrow(thin_999) > 0) {
    thin_rates <- sort(unique(thin_999$offered_mps))
    cat(sprintf(
      paste0("p99.9 is under-supported at %d of %d rungs (offered rates: %s).\n\n",
             "At those rates a 30 s repetition yields too few observations for the ",
             "0.1%% tail to be stable -- the reported p99.9 moves with which handful ",
             "of samples landed slowest, not with the transport. Quote p50 and p99 ",
             "at these rungs and treat p99.9 as directional only. The fix, if the ",
             "tail at low rate is the question, is a longer runtime rather than more ",
             "repetitions: percentiles are computed per run, so three short runs give ",
             "three noisy estimates rather than one good one.\n\n"),
      nrow(thin_999), nrow(tail_support),
      paste(format(thin_rates, big.mark = ",", trim = TRUE), collapse = ", ")))
  }

  kable(tail_support, caption = sprintf(
    "Observations behind each reported percentile, per repetition. Samples are the replies sockperf received; p99/p99.9 columns are the count in each tail. A tail with fewer than %d samples is marked thin and should not carry a quantitative claim.",
    ul_min_tail_samples))
}
```

```{r latency-rate-idle-state}
idle_grouping <- sql("
-- Cast before coalescing with a string sentinel. These are 0/1 flags, so
-- read_csv_auto infers INT64 once any run has recorded them and VARCHAR while
-- they are all empty -- meaning the same query binds in one result set and
-- fails in another. The cast makes the column type independent of which runs
-- happen to be present.
select coalesce(cast(cpu_idle_pinning_requested as varchar), '0') as pinning_requested,
       coalesce(cast(cpu_idle_pinning_supported as varchar), 'unknown') as pinning_supported,
       coalesce(cast(cpu_idle_pinning_verified as varchar), 'unknown') as pinning_verified,
       count(distinct scenario_name) as scenarios,
       count(*) as rows
from sockperf
where mode = 'ul'
group by 1, 2, 3
order by 1, 2, 3
")
if (nrow(idle_grouping) == 0) {
  no_data("No under-load rows to group by idle-state control.")
} else {
  kable(idle_grouping, caption = "CPU idle-state control behind these measurements. Not every instance type exposes the knob; rows with pinning_supported = 0 have idle-exit latency in their low-rate numbers and must not be pooled with pinned rows.")
}
```

## Data Quality

Two checks that decide whether anything above can be quoted.

```{r data-quality-failures}
# Failures are reported across every arm including controls: a control that
# could not run is itself a data-quality finding.
fail_summary <- sql("
select run_id, scenario_name, benchmark_name, count(*) as failed_repetitions,
       min(failure_reason) as example_reason
from failures
group by 1, 2, 3
order by failed_repetitions desc, 1, 2, 3
")
if (nrow(fail_summary) == 0) {
  cat("No failed repetitions recorded: every repetition produced a usable measurement.\n")
} else {
  kable(fail_summary, caption = "Repetitions that produced no usable measurement. These are invisible in the tables above, which contain only rows that parsed, so a benchmark can look complete while having lost most of its repetitions.")
}
```

```{r data-quality-fragmentation}
# A UDP datagram larger than one frame is split into IP fragments, and losing
# any fragment loses the whole datagram. TCP at the same message size segments
# cleanly with independent loss recovery. So a TCP-vs-UDP comparison above the
# frame capacity is partly a comparison of fragmentation, and whether it applies
# depends on the MTU of the arm -- which differs by provider and by path.
frag <- sql("
select scenario_name, provider, placement_class, protocol, msg_size_bytes,
       primary_iface_mtu as client_mtu,
       server_primary_iface_mtu as server_mtu,
       count(*) as n
from sockperf
where protocol = 'udp'
group by 1, 2, 3, 4, 5, 6, 7
order by 1, 4, 5
")
if (nrow(frag) == 0) {
  cat("No UDP sockperf rows.\n")
} else if (all(is.na(frag$client_mtu))) {
  cat("MTU was not recorded for these runs, so fragmentation cannot be checked.",
      "Runs made before node-facts.env existed have no MTU; re-run to populate it.\n")
} else {
  # IPv4 header 20 + UDP header 8.
  frag$frame_capacity_bytes <- frag$client_mtu - 28
  frag$ip_fragments <- ceiling(frag$msg_size_bytes / frag$frame_capacity_bytes)
  frag$mtu_mismatch <- !is.na(frag$server_mtu) & frag$client_mtu != frag$server_mtu
  flagged <- frag[!is.na(frag$ip_fragments) & (frag$ip_fragments > 1 | frag$mtu_mismatch), ]
  # Note first, so kable() can be the last expression and get knitr's table
  # treatment; see the purchase-model chunk for why print(kable(...)) does not.
  cat("Note: this is the *interface* MTU. The path MTU can be lower, especially across regions or peered networks, and is not measured here.\n\n")
  if (nrow(flagged) == 0) {
    cat("Every UDP message fits in a single frame at the recorded MTU, and client and server MTUs agree.\n")
  } else {
    kable(flagged, caption = "UDP rows that fragment at the recorded MTU, or whose two ends disagree on MTU. Latency at these sizes is not directly comparable with TCP, nor across arms with different MTUs.")
  }
}
```

```{r data-quality-purchase-model}
# Spot draws from spare capacity, so it influences which physical host an
# instance lands on. Spot and on-demand are the same hardware, but host draw is
# not a free variable at these effect sizes, so a comparison spanning both
# models has an uncontrolled term in it. Read from instance metadata, so this
# reflects what the instance was rather than what was requested.
purchase <- sql("
select coalesce(purchase_model, 'not recorded') as client_model,
       coalesce(server_purchase_model, 'not recorded') as server_model,
       count(distinct scenario_name) as scenarios,
       count(*) as rows
from sockperf
group by 1, 2
order by 1, 2
")
if (nrow(purchase) == 0) {
  cat("No sockperf rows.\n")
} else {
  distinct_models <- setdiff(unique(c(purchase$client_model, purchase$server_model)), "not recorded")
  # The warning is emitted first so that kable() is the last expression in the
  # block. knitr only gives a kable object its table treatment when it is
  # auto-printed; wrapping it in print() emits the markdown as verbatim console
  # output instead, which renders as a code block rather than a table.
  if (length(distinct_models) > 1) {
    cat(sprintf("WARNING: this result set spans %s. Keep every arm of a comparison on one purchasing model, or the host draw differs between arms.\n\n",
                paste(distinct_models, collapse = " and ")))
  }
  kable(purchase, caption = "Purchase model of the instances behind these measurements, read from the metadata service.")
}
```

```{r data-quality-within-scenario}
# The two noise figures answer different questions and an effect has to clear
# the right one.
#
#   within-scenario  repetitions of one benchmark on one provisioned pair:
#                    same instances, same boot, minutes apart.
#   control drift    the same scenario re-provisioned at the end of the matrix:
#                    different instances, different hosts, hours apart.
#
# Because scenarios are destroyed and re-provisioned, the control includes which
# hardware you drew. That is the figure a cross-scenario comparison must beat;
# the within-scenario spread only bounds noise inside one provisioning.
within <- sql("
select scenario_name, protocol, benchmark_name,
       count(*) as reps,
       round(median(p50_rtt_us), 1) as median_p50,
       round(100.0 * stddev_samp(p50_rtt_us) / nullif(avg(p50_rtt_us), 0), 1) as p50_cv_pct,
       round(100.0 * stddev_samp(p99_rtt_us) / nullif(avg(p99_rtt_us), 0), 1) as p99_cv_pct
from sockperf
group by 1, 2, 3
having count(*) > 1
order by p50_cv_pct desc nulls last
")
if (nrow(within) == 0) {
  cat("No benchmark has more than one repetition, so within-scenario noise cannot be estimated.\n")
} else {
  kable(head(within, 20), caption = "Within-scenario spread across repetitions (worst 20 by p50 CV). This bounds noise inside a single provisioning; it is not the bar for comparing two scenarios -- use the reversal-control drift below for that.")
}
```

```{r data-quality-control}
# Reads sockperf_all, not the control-free view, and matches the suffix with
# ends_with rather than LIKE: in SQL LIKE, '_' is a single-character wildcard, so
# '%__control' also matches names such as 'foo-XXcontrol'.
control_drift <- sql("
select s.base_scenario_name as scenario,
       s.protocol, s.benchmark_name,
       round(median(case when s.is_control then s.p50_rtt_us end), 1) as control_p50,
       round(median(case when not s.is_control then s.p50_rtt_us end), 1) as original_p50,
       round(median(case when s.is_control then s.p99_rtt_us end), 1) as control_p99,
       round(median(case when not s.is_control then s.p99_rtt_us end), 1) as original_p99
from sockperf_all s
where s.base_scenario_name in (
  select base_scenario_name from sockperf_all where is_control
)
group by 1, 2, 3
order by 1, 2, 3
")
if (nrow(control_drift) == 0) {
  cat("No reversal control arm in this result set. Run with --reversal-control to measure how far the apparatus drifted over the matrix; without it there is no noise floor to compare effects against.\n")
} else {
  control_drift$p50_drift_pct <- round(100 * (control_drift$control_p50 - control_drift$original_p50) / control_drift$original_p50, 1)
  control_drift$p99_drift_pct <- round(100 * (control_drift$control_p99 - control_drift$original_p99) / control_drift$original_p99, 1)
  kable(control_drift, caption = "Reversal control: the same scenario re-run at the end of the matrix. This drift is the measured noise floor. An effect reported above that is smaller than the drift here has not been demonstrated.")
}
```
