---
title: "Storage Benchmark Analysis"
params:
  result_id: "all"
  note: null
  config_file: null
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 13,
  fig.height = 8
)

rmd_dir <- dirname(normalizePath(knitr::current_input(dir = TRUE)))
repo_root <- normalizePath(file.path(rmd_dir, "..", ".."))

source(file.path(repo_root, "analysis", "storage", "prelude.r"))
options(scipen = 999)

result_id <- params$result_id
results_dir <- file.path(repo_root, "analysis", "storage", result_id)

required_csvs <- c(
  "storage_scenarios.csv",
  "storage_benchmarks.csv",
  "storage_fio.csv",
  "storage_failures.csv"
)

if (!all(file.exists(file.path(results_dir, required_csvs)))) {
  stop(sprintf("Missing storage CSVs in %s. Run analysis/storage/build_csv.R first.", results_dir))
}

csv_sql_path <- function(name) {
  gsub("'", "''", normalizePath(file.path(results_dir, name), mustWork = TRUE), fixed = TRUE)
}

sql("select 1")
con <- duckdbcons[[":memory:"]]
DBI::dbExecute(con, "drop table if exists scenarios")
DBI::dbExecute(con, "drop table if exists benchmarks")
DBI::dbExecute(con, "drop table if exists fio")
DBI::dbExecute(con, "drop table if exists fio_all")
DBI::dbExecute(con, "drop table if exists failures")
DBI::dbExecute(con, sprintf("create table scenarios as select * from read_csv_auto('%s')", csv_sql_path("storage_scenarios.csv")))
DBI::dbExecute(con, sprintf("create table benchmarks as select * from read_csv_auto('%s')", csv_sql_path("storage_benchmarks.csv")))
DBI::dbExecute(con, sprintf("create table fio_all as select * from read_csv_auto('%s')", csv_sql_path("storage_fio.csv")))
DBI::dbExecute(con, "
create view fio as
select *
from fio_all
where coalesce(durability_mode, 'none') = 'none'
  and coalesce(durability_every_ops, 0) = 0
")
DBI::dbExecute(con, sprintf("create table failures as select * from read_csv_auto('%s')", csv_sql_path("storage_failures.csv")))

merge_lists <- function(base, overrides) {
  if (is.null(overrides) || length(overrides) == 0) return(base)
  out <- base
  for (name in names(overrides)) out[[name]] <- overrides[[name]]
  out
}

as_char_vec <- function(x) {
  if (is.null(x) || length(x) == 0) return(character(0))
  unique(as.character(unlist(x, use.names = FALSE)))
}

default_report_config <- list(
  reference_machine_type = NULL,
  instance_comparison_block_performance_class = NULL,
  local_instance_comparison_block_performance_class = NULL,
  reference_block_performance_class = NULL,
  reference_block_filesystem = NULL,
  reference_local_filesystem = NULL,
  reference_os_tuning = "standard",
  local_instance_rw_mode = "randread",
  throughput_reference_io_engine = "io_uring",
  throughput_reference_block_size = "128k",
  throughput_reference_iodepth = 16,
  throughput_reference_numjobs = 1,
  iops_reference_io_engine = "io_uring",
  iops_reference_block_size = "4k",
  iops_reference_iodepth = 32,
  iops_reference_numjobs = 1,
  latency_reference_io_engine = "psync",
  latency_reference_block_size = "4k",
  latency_reference_iodepth = 1,
  latency_reference_numjobs = 1,
  durability_reference_io_engine = "psync",
  durability_reference_block_size = "4k",
  durability_reference_iodepth = 1,
  durability_reference_numjobs = 1,
  reference_durability_mode = "none",
  reference_durability_every_ops = 0,
  psync_iodepth = 1,
  psync_numjobs = 1,
  block_size_comparison = data.frame(
    block_size = c("4k", "128k"),
    iodepth = c(32, 16),
    stringsAsFactors = FALSE
  ),
  preferred_machine_order = c("g2a.60d", "g2a.30d", "g2a.8d", "g2a.120d", "c6id.metal", "c6id.32xlarge"),
  preferred_workload_order = c("randread", "randwrite", "read", "write"),
  preferred_engine_order = c("psync", "io_uring"),
  preferred_target_order = c("local", "block"),
  preferred_filesystem_order = c("raw", "xfs", "ext4"),
  provider_overrides = list(
    stackit = list(
      reference_machine_type = "g2a.60d",
      instance_comparison_block_performance_class = "storage_premium_perf12",
      local_instance_comparison_block_performance_class = "storage_premium_perf6",
      reference_block_performance_class = "storage_premium_perf29",
      reference_block_filesystem = "xfs",
      reference_local_filesystem = "xfs",
      reference_os_tuning = "standard",
      performance_class_machine_types = c("g2a.8d", "g2a.30d", "g2a.60d", "g2a.120d")
    ),
    aws = list(
      reference_machine_type = "c6id.metal",
      instance_comparison_block_performance_class = "storage_premium_perf29",
      local_instance_comparison_block_performance_class = "storage_premium_perf29",
      reference_block_performance_class = "storage_premium_perf29",
      reference_block_filesystem = "xfs",
      reference_local_filesystem = "xfs",
      reference_os_tuning = "standard",
      performance_class_machine_types = c("c6id.32xlarge", "c6id.metal")
    )
  )
)

report_config <- default_report_config
if (!is.null(params$config_file) && nzchar(params$config_file)) {
  config_override <- jsonlite::fromJSON(params$config_file, simplifyDataFrame = TRUE)
  unknown_keys <- setdiff(names(config_override), names(default_report_config))
  if (length(unknown_keys) > 0) {
    stop(sprintf("Unknown storage report config keys: %s", paste(unknown_keys, collapse = ", ")))
  }
  if ("provider_overrides" %in% names(config_override)) {
    report_config$provider_overrides <- merge_lists(report_config$provider_overrides, config_override$provider_overrides)
    config_override$provider_overrides <- NULL
  }
  report_config <- merge_lists(report_config, config_override)
}

quote_sql <- function(x) as.character(DBI::dbQuoteString(con, x))

providers <- sql("
select distinct provider
from scenarios
where provider is not null and provider <> ''
order by 1
")$provider

if (length(providers) == 0) {
  stop("No storage providers were discovered in storage_scenarios.csv")
}

provider_label <- function(provider) {
  switch(
    provider,
    aws = "AWS",
    stackit = "Stackit",
    provider
  )
}

provider_distinct <- function(provider, table_name, column, extra_where = "1=1", order_by = "1") {
  provider_literal <- quote_sql(provider)
  sql(glue::glue("
  select distinct {column} as value
  from {table_name}
  where provider = {provider_literal}
    and {column} is not null
    and cast({column} as varchar) <> ''
    and {extra_where}
  order by {order_by}
  "))$value
}

resolve_scalar <- function(current, available, preferred = character(0)) {
  available <- as_char_vec(available)
  preferred <- as_char_vec(preferred)
  if (length(available) == 0) return(current)
  if (!is.null(current) && length(current) == 1 && !is.na(current) && current %in% available) return(current)
  preferred_hits <- preferred[preferred %in% available]
  if (length(preferred_hits) > 0) return(preferred_hits[[1]])
  available[[1]]
}

resolve_provider_config <- function(provider) {
  cfg <- report_config
  provider_override <- report_config$provider_overrides[[provider]]
  cfg$provider_overrides <- NULL
  cfg <- merge_lists(cfg, provider_override)

  machine_types <- provider_distinct(provider, "fio", "benchmark_machine_type")
  perf_classes <- provider_distinct(provider, "fio", "block_volume_performance_class")
  workloads <- provider_distinct(provider, "fio", "benchmark_rw_mode")
  engines <- provider_distinct(provider, "fio", "io_engine")
  targets <- provider_distinct(provider, "fio", "storage_target")
  filesystems <- provider_distinct(provider, "fio", "storage_target_filesystem")
  block_filesystems <- provider_distinct(provider, "fio", "storage_target_filesystem", "storage_target = 'block'")
  local_filesystems <- provider_distinct(provider, "fio", "storage_target_filesystem", "storage_target = 'local'")
  tunings <- provider_distinct(provider, "fio", "os_tuning")

  cfg$reference_machine_type <- resolve_scalar(
    cfg$reference_machine_type,
    machine_types,
    cfg$preferred_machine_order
  )
  cfg$instance_comparison_block_performance_class <- resolve_scalar(
    cfg$instance_comparison_block_performance_class,
    perf_classes,
    perf_classes
  )
  cfg$local_instance_comparison_block_performance_class <- resolve_scalar(
    cfg$local_instance_comparison_block_performance_class,
    perf_classes,
    perf_classes
  )
  cfg$reference_block_performance_class <- resolve_scalar(
    cfg$reference_block_performance_class,
    perf_classes,
    perf_classes
  )
  cfg$reference_block_filesystem <- resolve_scalar(
    cfg$reference_block_filesystem,
    block_filesystems,
    c("xfs", "ext4", "raw")
  )
  cfg$reference_local_filesystem <- resolve_scalar(
    cfg$reference_local_filesystem,
    local_filesystems,
    c("xfs", "ext4", "raw")
  )
  cfg$reference_os_tuning <- resolve_scalar(
    cfg$reference_os_tuning,
    tunings,
    c("standard", "tuned")
  )
  cfg$local_instance_rw_mode <- resolve_scalar(
    cfg$local_instance_rw_mode,
    workloads,
    cfg$preferred_workload_order
  )
  cfg$throughput_reference_io_engine <- resolve_scalar(
    cfg$throughput_reference_io_engine,
    engines,
    cfg$preferred_engine_order
  )
  cfg$iops_reference_io_engine <- resolve_scalar(
    cfg$iops_reference_io_engine,
    engines,
    cfg$preferred_engine_order
  )
  cfg$latency_reference_io_engine <- resolve_scalar(
    cfg$latency_reference_io_engine,
    engines,
    cfg$preferred_engine_order
  )
  cfg$performance_class_machine_types <- unique(c(
    cfg$performance_class_machine_types[cfg$performance_class_machine_types %in% machine_types],
    machine_types
  ))
  cfg$machine_levels <- unique(c(
    cfg$preferred_machine_order[cfg$preferred_machine_order %in% machine_types],
    machine_types
  ))
  cfg$workload_levels <- unique(c(
    cfg$preferred_workload_order[cfg$preferred_workload_order %in% workloads],
    workloads
  ))
  cfg$engine_levels <- unique(c(
    cfg$preferred_engine_order[cfg$preferred_engine_order %in% engines],
    engines
  ))
  cfg$target_levels <- unique(c(
    cfg$preferred_target_order[cfg$preferred_target_order %in% targets],
    targets
  ))
  cfg$filesystem_levels <- unique(c(
    cfg$preferred_filesystem_order[cfg$preferred_filesystem_order %in% filesystems],
    filesystems
  ))
  cfg
}

provider_configs <- setNames(lapply(providers, resolve_provider_config), providers)
block_size_comparison_values_sql <- paste(
  sprintf("('%s', %s)", report_config$block_size_comparison$block_size, report_config$block_size_comparison$iodepth),
  collapse = ", "
)

perf_class_order <- sql("
select distinct block_volume_performance_class
from scenarios
where block_volume_performance_class is not null
order by block_volume_performance_class
")$block_volume_performance_class
perf_class_rank <- ifelse(
  grepl("^storage_premium_perf[0-9]+$", perf_class_order),
  as.integer(sub(".*perf([0-9]+).*", "\\1", perf_class_order)),
  Inf
)
perf_class_order <- perf_class_order[order(perf_class_rank, perf_class_order)]
stackit_profile_iops <- c(
  storage_premium_perf0 = 120,
  storage_premium_perf1 = 500,
  storage_premium_perf2 = 1000,
  storage_premium_perf4 = 2000,
  storage_premium_perf6 = 5000,
  storage_premium_perf8 = 10000,
  storage_premium_perf10 = 15000,
  storage_premium_perf12 = 20000,
  storage_premium_perf13 = 20000,
  storage_premium_perf14 = 25000,
  storage_premium_perf15 = 25000,
  storage_premium_perf16 = 30000,
  storage_premium_perf17 = 30000,
  storage_premium_perf18 = 35000,
  storage_premium_perf19 = 35000,
  storage_premium_perf20 = 40000,
  storage_premium_perf21 = 40000,
  storage_premium_perf29 = 60000
)
stackit_profile_throughput_mbps <- c(
  storage_premium_perf0 = 25,
  storage_premium_perf1 = 50,
  storage_premium_perf2 = 100,
  storage_premium_perf4 = 150,
  storage_premium_perf6 = 200,
  storage_premium_perf8 = 250,
  storage_premium_perf10 = 300,
  storage_premium_perf12 = 350,
  storage_premium_perf13 = 700,
  storage_premium_perf14 = 400,
  storage_premium_perf15 = 800,
  storage_premium_perf16 = 450,
  storage_premium_perf17 = 900,
  storage_premium_perf18 = 500,
  storage_premium_perf19 = 1000,
  storage_premium_perf20 = 550,
  storage_premium_perf21 = 1100,
  storage_premium_perf29 = 1500
)

format_performance_class_value <- function(provider, perf_class, block_volume_type = NA, block_volume_iops = NA, block_volume_throughput_mbps = NA) {
  perf_class <- as.character(perf_class %||% NA_character_)
  if (is.na(perf_class) || !nzchar(perf_class)) return(NA_character_)
  if (!identical(provider, "aws")) {
    if (!is.na(block_volume_iops) && !is.na(block_volume_throughput_mbps)) {
      return(sprintf("%s (%s IOPS | %s MiB/s)", perf_class, format(round(block_volume_iops, 0), big.mark = ","), format(round(block_volume_throughput_mbps, 0), big.mark = ",")))
    }
    return(perf_class)
  }
  if (is.na(block_volume_type) || !nzchar(as.character(block_volume_type)) || is.na(block_volume_iops) || is.na(block_volume_throughput_mbps)) {
    return(perf_class)
  }
  sprintf("%s (%s IOPS | %s MiB/s)", as.character(block_volume_type), format(round(block_volume_iops, 0), big.mark = ","), format(round(block_volume_throughput_mbps, 0), big.mark = ","))
}

apply_performance_class_display <- function(df, provider = NULL) {
  if (!("block_volume_performance_class" %in% names(df))) return(df)
  provider_values <- if ("provider" %in% names(df)) as.character(df$provider) else rep_len(provider %||% NA_character_, nrow(df))
  block_types <- if ("block_volume_type" %in% names(df)) df$block_volume_type else rep_len(NA_character_, nrow(df))
  block_iops <- if ("block_volume_iops" %in% names(df)) df$block_volume_iops else rep_len(NA_real_, nrow(df))
  block_throughput <- if ("block_volume_throughput_mbps" %in% names(df)) df$block_volume_throughput_mbps else rep_len(NA_real_, nrow(df))
  df$block_volume_performance_class_raw <- as.character(df$block_volume_performance_class)
  df$block_volume_performance_class <- vapply(
    seq_len(nrow(df)),
    function(i) format_performance_class_value(
      provider = provider_values[[i]],
      perf_class = df$block_volume_performance_class_raw[[i]],
      block_volume_type = block_types[[i]],
      block_volume_iops = block_iops[[i]],
      block_volume_throughput_mbps = block_throughput[[i]]
    ),
    character(1)
  )
  df
}

display_perf_class_order <- vapply(
  perf_class_order,
  function(perf_class) format_performance_class_value(
    "stackit",
    perf_class,
    block_volume_iops = if (perf_class %in% names(stackit_profile_iops)) unname(stackit_profile_iops[[perf_class]]) else NA_real_,
    block_volume_throughput_mbps = if (perf_class %in% names(stackit_profile_throughput_mbps)) unname(stackit_profile_throughput_mbps[[perf_class]]) else NA_real_
  ),
  character(1)
)

durability_order_key <- function(label) {
  if (is.na(label) || !nzchar(label)) return(9999)
  if (identical(label, "none")) return(0)
  parts <- strsplit(label, "/", fixed = TRUE)[[1]]
  mode <- parts[[1]]
  every_ops <- suppressWarnings(as.numeric(parts[[2]] %||% NA))
  mode_rank <- switch(mode, fsync = 1, fdatasync = 2, 9)
  mode_rank * 100000 + ifelse(is.na(every_ops), 99999, every_ops)
}

durability_label_levels <- function(values) {
  values <- unique(as.character(values))
  values <- values[!is.na(values) & nzchar(values)]
  if (length(values) == 0) return("none")
  values[order(vapply(values, durability_order_key, numeric(1)))]
}

durability_label_from_fields <- function(mode, every_ops) {
  mode <- as.character(mode %||% "none")
  if (is.na(mode) || !nzchar(mode) || identical(mode, "none")) return("none")
  every_ops <- suppressWarnings(as.numeric(every_ops))
  if (is.na(every_ops) || every_ops <= 0) return(mode)
  sprintf("%s/%s", mode, format(every_ops, trim = TRUE, scientific = FALSE))
}

baseline_durability_clause <- function(alias = NULL, indent = "    ") {
  prefix <- if (is.null(alias) || !nzchar(alias)) "" else paste0(alias, ".")
  paste0(
    indent, "and coalesce(", prefix, "durability_mode, 'none') = 'none'\n",
    indent, "and coalesce(", prefix, "durability_every_ops, 0) = 0"
  )
}

apply_factor_levels <- function(df, provider = NULL) {
  df <- apply_performance_class_display(df, provider = provider)
  cfg <- if (!is.null(provider)) provider_configs[[provider]] else NULL
  machine_levels <- if (!is.null(cfg)) cfg$machine_levels else unique(c(
    report_config$preferred_machine_order,
    sql("select distinct benchmark_machine_type from fio where benchmark_machine_type is not null order by 1")$benchmark_machine_type
  ))
  workload_levels <- if (!is.null(cfg)) cfg$workload_levels else unique(c(
    report_config$preferred_workload_order,
    sql("select distinct benchmark_rw_mode from fio where benchmark_rw_mode is not null order by 1")$benchmark_rw_mode
  ))
  engine_levels <- if (!is.null(cfg)) cfg$engine_levels else unique(c(
    report_config$preferred_engine_order,
    sql("select distinct io_engine from fio where io_engine is not null order by 1")$io_engine
  ))
  target_levels <- if (!is.null(cfg)) cfg$target_levels else unique(c(
    report_config$preferred_target_order,
    sql("select distinct storage_target from fio where storage_target is not null order by 1")$storage_target
  ))
  filesystem_levels <- if (!is.null(cfg)) cfg$filesystem_levels else unique(c(
    report_config$preferred_filesystem_order,
    sql("select distinct storage_target_filesystem from fio where storage_target_filesystem is not null order by 1")$storage_target_filesystem
  ))
  block_size_levels <- sql("select distinct block_size, block_size_bytes from fio where block_size is not null order by block_size_bytes")$block_size

  if ("benchmark_machine_type" %in% names(df)) df$benchmark_machine_type <- factor(df$benchmark_machine_type, levels = machine_levels)
  if ("benchmark_rw_mode" %in% names(df)) df$benchmark_rw_mode <- factor(df$benchmark_rw_mode, levels = workload_levels)
  if ("io_engine" %in% names(df)) df$io_engine <- factor(df$io_engine, levels = engine_levels)
  if ("storage_target" %in% names(df)) df$storage_target <- factor(df$storage_target, levels = target_levels)
  if ("storage_target_filesystem" %in% names(df)) df$storage_target_filesystem <- factor(df$storage_target_filesystem, levels = filesystem_levels)
  if ("block_size" %in% names(df)) df$block_size <- factor(df$block_size, levels = block_size_levels)
  if ("block_volume_performance_class" %in% names(df)) {
    perf_levels <- unique(c(display_perf_class_order, as.character(df$block_volume_performance_class)))
    df$block_volume_performance_class <- factor(df$block_volume_performance_class, levels = perf_levels)
  }
  if ("durability_label" %in% names(df)) {
    df$durability_label <- factor(df$durability_label, levels = durability_label_levels(df$durability_label))
  }
  if ("durability_mode" %in% names(df)) {
    df$durability_mode <- factor(df$durability_mode, levels = c("none", "fsync", "fdatasync"))
  }
  if ("latency_metric" %in% names(df)) df$latency_metric <- factor(df$latency_metric, levels = c("avg", "p50", "p99", "p99.9"))
  if ("execution_config" %in% names(df)) df$execution_config <- factor(df$execution_config, levels = unique(df$execution_config))
  df
}

wrap_subtitle <- function(text, width = 88) {
  if (is.null(text) || !nzchar(text)) return(NULL)
  paste(strwrap(text, width = width), collapse = "\n")
}

box_label_accuracy <- function(values, percent = FALSE) {
  finite_values <- values[is.finite(values)]
  if (length(finite_values) == 0) return(1)
  max_abs <- max(abs(finite_values), na.rm = TRUE)
  if (percent) {
    if (max_abs >= 10) return(0.1)
    if (max_abs >= 1) return(0.01)
    return(0.001)
  }
  if (max_abs >= 1000) return(1)
  if (max_abs >= 100) return(0.1)
  if (max_abs >= 10) return(0.1)
  if (max_abs >= 1) return(0.01)
  if (max_abs >= 0.1) return(0.001)
  0.0001
}

format_box_median_labels <- function(values, y, ylab = NULL) {
  percent_metric <- identical(y, "lost_percent") || (!is.null(ylab) && grepl("%", ylab, fixed = TRUE))
  accuracy <- box_label_accuracy(values, percent = percent_metric)
  formatter <- if (percent_metric) {
    label_percent(scale = 1, accuracy = accuracy)
  } else {
    label_number(accuracy = accuracy, big.mark = ",", trim = TRUE)
  }
  formatter(values)
}

build_box_median_annotation <- function(df, x, y, fill = NULL, facet_cols = NULL, formatter = NULL,
                                        max_boxes_per_panel = 8, max_panels = 16, max_labels = 48) {
  required_cols <- unique(c(x, y, fill, facet_cols))
  plot_df <- df[stats::complete.cases(df[, required_cols, drop = FALSE]), required_cols, drop = FALSE]
  if (nrow(plot_df) == 0) return(list(enabled = FALSE, data = NULL, upper_expand = 0.06))

  group_cols <- unique(c(facet_cols, x, fill))
  split_key <- interaction(plot_df[, group_cols, drop = FALSE], drop = TRUE, lex.order = TRUE, sep = "\r")
  label_groups <- split(plot_df, split_key, drop = TRUE)
  label_rows <- lapply(label_groups, function(group_df) {
    row <- group_df[1, group_cols, drop = FALSE]
    row$median_value <- stats::median(group_df[[y]], na.rm = TRUE)
    row
  })
  label_df <- do.call(rbind, label_rows)
  rownames(label_df) <- NULL

  if (length(facet_cols) == 0) {
    panel_range_df <- data.frame(panel_min = min(plot_df[[y]], na.rm = TRUE), panel_max = max(plot_df[[y]], na.rm = TRUE))
    label_df$panel_min <- panel_range_df$panel_min[[1]]
    label_df$panel_max <- panel_range_df$panel_max[[1]]
    panel_count <- 1L
    boxes_per_panel <- nrow(label_df)
  } else {
    panel_split_key <- interaction(plot_df[, facet_cols, drop = FALSE], drop = TRUE, lex.order = TRUE, sep = "\r")
    panel_groups <- split(plot_df, panel_split_key, drop = TRUE)
    panel_rows <- lapply(panel_groups, function(group_df) {
      row <- group_df[1, facet_cols, drop = FALSE]
      row$panel_min <- min(group_df[[y]], na.rm = TRUE)
      row$panel_max <- max(group_df[[y]], na.rm = TRUE)
      row
    })
    panel_range_df <- do.call(rbind, panel_rows)
    rownames(panel_range_df) <- NULL
    label_df <- merge(label_df, panel_range_df, by = facet_cols, sort = FALSE)
    panel_label_counts <- vapply(split(label_df, interaction(label_df[, facet_cols, drop = FALSE], drop = TRUE, lex.order = TRUE, sep = "\r")), nrow, integer(1))
    panel_count <- length(panel_label_counts)
    boxes_per_panel <- max(panel_label_counts)
  }

  label_df$panel_span <- pmax(label_df$panel_max - label_df$panel_min, 0)
  label_df$label_nudge <- pmax(label_df$panel_span * 0.03, pmax(abs(label_df$median_value), 1) * 0.01)
  label_df$label_y <- label_df$median_value + label_df$label_nudge
  label_df$label <- if (is.null(formatter)) as.character(label_df$median_value) else formatter(label_df$median_value)

  enabled <- nrow(label_df) > 0 &&
    boxes_per_panel <= max_boxes_per_panel &&
    panel_count <= max_panels &&
    nrow(label_df) <= max_labels

  list(
    enabled = enabled,
    data = label_df,
    upper_expand = if (enabled) 0.14 else 0.06
  )
}

add_box_median_labels <- function(plot_obj, annotation, x, fill = NULL, dodge_width = NULL, size = 3.8) {
  if (!annotation$enabled) return(plot_obj)
  mapping <- aes(x = .data[[x]], y = label_y, label = label)
  position <- position_identity()
  if (!is.null(fill) && !is.null(dodge_width)) {
    mapping <- aes(x = .data[[x]], y = label_y, label = label, group = .data[[fill]])
    position <- position_dodge(width = dodge_width)
  }
  plot_obj +
    geom_text(
      data = annotation$data,
      mapping = mapping,
      inherit.aes = FALSE,
      position = position,
      vjust = 0,
      size = size,
      color = colors[["carbon"]],
      check_overlap = TRUE,
      show.legend = FALSE
    )
}

metric_box <- function(df, x, y, provider, fill = NULL, facet = "benchmark_rw_mode", title = NULL,
                       subtitle = NULL, ylab = NULL, ncol = 2, y_zero = TRUE) {
  if (nrow(df) == 0) return(show_no_data_plot("No data for this comparison."))
  df <- apply_factor_levels(df, provider = provider)
  facet_cols <- if (is.null(facet)) NULL else facet
  annotation <- build_box_median_annotation(
    df,
    x,
    y,
    fill = fill,
    facet_cols = facet_cols,
    formatter = function(values) format_box_median_labels(values, y, ylab)
  )
  mapping <- if (is.null(fill)) {
    aes(x = .data[[x]], y = .data[[y]])
  } else {
    aes(x = .data[[x]], y = .data[[y]], fill = .data[[fill]])
  }
  p <- ggplot(df, mapping) +
    geom_boxplot(outlier.shape = NA, alpha = 0.72) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    labs(title = title, subtitle = wrap_subtitle(subtitle), x = NULL, y = ylab, fill = NULL) +
    base_plot_theme()
  p <- add_box_median_labels(p, annotation, x)

  if (y_zero) {
    p <- p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, annotation$upper_expand)))
  } else {
    p <- p + scale_y_continuous(labels = comma, expand = expansion(mult = c(0.02, annotation$upper_expand)))
  }

  if (!is.null(facet)) {
    p <- p + facet_wrap(stats::as.formula(paste("~", facet)), ncol = ncol, scales = "fixed")
  }

  p + guides(fill = "none")
}

emit_heading <- function(level, title) {
  cat(sprintf("%s %s\n\n", paste(rep("#", level), collapse = ""), title))
}

emit_table <- function(df, caption, empty_message = "No data is available for this section.", provider = NULL) {
  if (nrow(df) == 0) {
    cat(empty_message, "\n\n")
  } else {
    df <- apply_performance_class_display(df, provider = provider)
    drop_cols <- intersect(c("block_volume_type", "block_volume_iops", "block_volume_throughput_mbps", "block_volume_performance_class_raw"), names(df))
    if ("block_volume_performance_class" %in% names(df) && length(drop_cols) > 0) {
      df <- df[, setdiff(names(df), drop_cols), drop = FALSE]
    }
    print(knitr::kable(df, caption = caption))
    cat("\n\n")
  }
}

resolve_reference_perf_label <- function(provider, perf_class) {
  if (is.null(perf_class) || is.na(perf_class) || !nzchar(perf_class)) return(NA_character_)
  provider_literal <- quote_sql(provider)
  perf_literal <- quote_sql(perf_class)
  ref_df <- sql(glue::glue("
  select provider, block_volume_performance_class, block_volume_type, block_volume_iops, block_volume_throughput_mbps
  from fio_all
  where provider = {provider_literal}
    and block_volume_performance_class = {perf_literal}
    and block_volume_performance_class is not null
  limit 1
  "))
  if (nrow(ref_df) == 0) {
    return(format_performance_class_value(provider, perf_class))
  }
  ref_df <- apply_performance_class_display(ref_df, provider = provider)
  as.character(ref_df$block_volume_performance_class[[1]])
}

provider_query <- function(provider, query) {
  provider_literal <- quote_sql(provider)
  sql(glue::glue(query, provider_literal = provider_literal))
}

filter_text <- function(provider, family) {
  cfg <- provider_configs[[provider]]
  ref_perf_label <- resolve_reference_perf_label(provider, cfg$reference_block_performance_class)
  if (identical(family, "throughput")) {
    sprintf(
      "Provider = %s, reference_machine_type = %s, reference performance class = %s, os_tuning = %s, io_engine = %s, block_size = %s, iodepth = %s, numjobs = %s, reference durability = %s/%s, reference block filesystem = %s, reference local filesystem = %s.",
      provider_label(provider), cfg$reference_machine_type, ref_perf_label, cfg$reference_os_tuning, cfg$throughput_reference_io_engine,
      cfg$throughput_reference_block_size, cfg$throughput_reference_iodepth, cfg$throughput_reference_numjobs,
      cfg$reference_durability_mode, cfg$reference_durability_every_ops,
      cfg$reference_block_filesystem, cfg$reference_local_filesystem
    )
  } else if (identical(family, "iops")) {
    sprintf(
      "Provider = %s, reference_machine_type = %s, reference performance class = %s, os_tuning = %s, block_size = %s, io_engine = %s, iodepth = %s, numjobs = %s, reference durability = %s/%s, reference block filesystem = %s, reference local filesystem = %s.",
      provider_label(provider), cfg$reference_machine_type, ref_perf_label, cfg$reference_os_tuning, cfg$iops_reference_block_size, cfg$iops_reference_io_engine,
      cfg$iops_reference_iodepth, cfg$iops_reference_numjobs, cfg$reference_durability_mode, cfg$reference_durability_every_ops,
      cfg$reference_block_filesystem, cfg$reference_local_filesystem
    )
  } else {
    sprintf(
      "Provider = %s, reference_machine_type = %s, reference performance class = %s, os_tuning = %s, block_size = %s, io_engine = %s, iodepth = %s, numjobs = %s, reference durability = %s/%s, reference block filesystem = %s, reference local filesystem = %s.",
      provider_label(provider), cfg$reference_machine_type, ref_perf_label, cfg$reference_os_tuning, cfg$latency_reference_block_size, cfg$latency_reference_io_engine,
      cfg$latency_reference_iodepth, cfg$latency_reference_numjobs, cfg$reference_durability_mode, cfg$reference_durability_every_ops,
      cfg$reference_block_filesystem, cfg$reference_local_filesystem
    )
  }
}

render_performance_class_plots_provider <- function(provider, metric_expression, ylab, title_suffix,
                                                    block_size_value, iodepth_value, io_engine_value, numjobs_value, heading_level = 4,
                                                    y_zero = TRUE) {
  cfg <- provider_configs[[provider]]
  provider_literal <- quote_sql(provider)
  machine_types <- cfg$performance_class_machine_types
  if (length(machine_types) == 0) {
    cat("No machine types are available for this comparison.\n\n")
    return(invisible(NULL))
  }
  for (machine_type in machine_types) {
    emit_heading(heading_level, machine_type)
    machine_literal <- quote_sql(machine_type)
    block_size_literal <- quote_sql(block_size_value)
    df <- provider_query(provider, glue::glue("
    select block_volume_performance_class, benchmark_rw_mode,
           block_volume_type, block_volume_iops, block_volume_throughput_mbps,
           {metric_expression} as metric_value
    from fio
    where provider = {provider_literal}
      and valid_measurement
      and os_tuning = {quote_sql(cfg$reference_os_tuning)}
      and benchmark_machine_type = {machine_literal}
      and storage_target = 'block'
      and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
      and io_engine = {quote_sql(io_engine_value)}
      and block_size = {block_size_literal}
      and iodepth = {iodepth_value}
      and numjobs = {numjobs_value}
{baseline_durability_clause()}
      and block_volume_performance_class is not null
    "))
    print(metric_box(
      df,
      x = "block_volume_performance_class",
      y = "metric_value",
      provider = provider,
      fill = "block_volume_performance_class",
      title = sprintf("%s block storage %s by performance class", machine_type, title_suffix),
      ylab = ylab,
      y_zero = y_zero
    ))
    cat("\n\n")
  }
}

render_filesystem_plot <- function(provider, storage_target, metric_expression, title, ylab,
                                   block_size, iodepth, io_engine, numjobs, y_zero = TRUE) {
  cfg <- provider_configs[[provider]]
  provider_literal <- quote_sql(provider)
  ref_machine <- quote_sql(cfg$reference_machine_type)
  ref_perf <- quote_sql(cfg$reference_block_performance_class)
  block_size_literal <- quote_sql(block_size)
  target_literal <- quote_sql(storage_target)
  df <- provider_query(provider, glue::glue("
  select storage_target_filesystem, benchmark_rw_mode,
         {metric_expression} as metric_value
  from fio_all
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {ref_machine}
    and block_volume_performance_class = {ref_perf}
    and storage_target = {target_literal}
    and storage_target_filesystem is not null
    and storage_target_filesystem <> ''
    and io_engine = {quote_sql(io_engine)}
    and block_size = {block_size_literal}
    and iodepth = {iodepth}
    and numjobs = {numjobs}
{baseline_durability_clause()}
  "))
  print(metric_box(
    df,
    x = "storage_target_filesystem",
    y = "metric_value",
    provider = provider,
    fill = "storage_target_filesystem",
    title = title,
    ylab = ylab,
    ncol = 2,
    y_zero = y_zero
  ))
  cat("\n\n")
}

render_durability_plot <- function(provider, storage_target, metric_expression, title, ylab,
                                   block_size, iodepth, io_engine, numjobs, y_zero = TRUE) {
  cfg <- provider_configs[[provider]]
  provider_literal <- quote_sql(provider)
  ref_machine <- quote_sql(cfg$reference_machine_type)
  ref_perf <- quote_sql(cfg$reference_block_performance_class)
  block_size_literal <- quote_sql(block_size)
  target_literal <- quote_sql(storage_target)
  target_filesystem <- if (identical(storage_target, "block")) cfg$reference_block_filesystem else cfg$reference_local_filesystem
  df <- provider_query(provider, glue::glue("
  select benchmark_rw_mode,
         case
           when coalesce(fio_fsync, 0) > 0 then concat('fsync/', cast(fio_fsync as varchar))
           when coalesce(fio_fdatasync, 0) > 0 then concat('fdatasync/', cast(fio_fdatasync as varchar))
           else 'none'
         end as durability_label,
         durability_mode,
         durability_every_ops,
         {metric_expression} as metric_value
  from fio_all
  where provider = {provider_literal}
    and valid_measurement
    and direction = 'write'
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {ref_machine}
    and block_volume_performance_class = {ref_perf}
    and storage_target = {target_literal}
    and storage_target_filesystem = {quote_sql(target_filesystem)}
    and io_engine = {quote_sql(io_engine)}
    and block_size = {block_size_literal}
    and iodepth = {iodepth}
    and numjobs = {numjobs}
  order by
    case
      when coalesce(durability_mode, 'none') = 'none' then 0
      when durability_mode = 'fsync' then 1
      when durability_mode = 'fdatasync' then 2
      else 9
    end,
    coalesce(durability_every_ops, 0)
  "))
  print(metric_box(
    df,
    x = "durability_label",
    y = "metric_value",
    provider = provider,
    fill = "durability_label",
    title = title,
    ylab = ylab,
    ncol = 1,
    y_zero = y_zero
  ))
  cat("\n\n")
}

provider_resolved_config <- function(provider) {
  cfg <- provider_configs[[provider]]
  data.frame(
    setting = c(
      "reference_machine_type",
      "instance_comparison_block_performance_class",
      "local_instance_comparison_block_performance_class",
      "reference_block_performance_class",
      "reference_block_filesystem",
      "reference_local_filesystem",
      "reference_os_tuning",
      "local_instance_rw_mode",
      "throughput_reference_io_engine",
      "throughput_reference_block_size",
      "throughput_reference_iodepth",
      "throughput_reference_numjobs",
      "iops_reference_io_engine",
      "iops_reference_block_size",
      "iops_reference_iodepth",
      "iops_reference_numjobs",
      "latency_reference_io_engine",
      "latency_reference_block_size",
      "latency_reference_iodepth",
      "latency_reference_numjobs",
      "durability_reference_io_engine",
      "durability_reference_block_size",
      "durability_reference_iodepth",
      "durability_reference_numjobs",
      "reference_durability_mode",
      "reference_durability_every_ops",
      "psync_iodepth",
      "psync_numjobs",
      "available_filesystems"
    ),
    value = c(
      cfg$reference_machine_type,
      resolve_reference_perf_label(provider, cfg$instance_comparison_block_performance_class),
      resolve_reference_perf_label(provider, cfg$local_instance_comparison_block_performance_class),
      resolve_reference_perf_label(provider, cfg$reference_block_performance_class),
      cfg$reference_block_filesystem,
      cfg$reference_local_filesystem,
      cfg$reference_os_tuning,
      cfg$local_instance_rw_mode,
      cfg$throughput_reference_io_engine,
      cfg$throughput_reference_block_size,
      cfg$throughput_reference_iodepth,
      cfg$throughput_reference_numjobs,
      cfg$iops_reference_io_engine,
      cfg$iops_reference_block_size,
      cfg$iops_reference_iodepth,
      cfg$iops_reference_numjobs,
      cfg$latency_reference_io_engine,
      cfg$latency_reference_block_size,
      cfg$latency_reference_iodepth,
      cfg$latency_reference_numjobs,
      cfg$durability_reference_io_engine,
      cfg$durability_reference_block_size,
      cfg$durability_reference_iodepth,
      cfg$durability_reference_numjobs,
      cfg$reference_durability_mode,
      cfg$reference_durability_every_ops,
      cfg$psync_iodepth,
      cfg$psync_numjobs,
      paste(cfg$filesystem_levels, collapse = ", ")
    ),
    stringsAsFactors = FALSE
  )
}
```

This report analyzes storage benchmark results from `r result_id`.

```{r note, results='asis', echo=FALSE}
if (!is.null(params$note) && nzchar(params$note)) {
  cat(sprintf("> %s\n\n", params$note))
}
```

The report is organized by provider. Each provider section keeps the same analysis hierarchy as the previous single-provider report and adds a `Filesystem Impact` subsection under `Throughput`, `IOPS`, and `Latency`. Outside the filesystem-impact sections, the plots fix a reference filesystem per target; those defaults are listed in the resolved configuration table for each provider.

```{r provider-sections, echo=FALSE, results='asis'}
for (provider in providers) {
  cfg <- provider_configs[[provider]]
  label <- provider_label(provider)
  provider_literal <- quote_sql(provider)

  emit_heading(1, label)

  emit_heading(2, "Overview")
  cat("All plots and tables in this section are filtered to one provider. Missing slices render as no-data sections instead of aborting the report.\n\n")

  coverage_counts <- provider_query(provider, "
  select
    (select count(*) from scenarios where provider = {provider_literal}) as scenarios,
    (select count(*) from benchmarks where provider = {provider_literal}) as benchmark_rows,
    (select count(*) from fio_all where provider = {provider_literal}) as fio_rows,
    (select count(*) from failures where provider = {provider_literal}) as failures,
    (select sum(case when valid_measurement then 1 else 0 end) from fio_all where provider = {provider_literal}) as valid_fio_rows
  ")
  emit_table(coverage_counts, sprintf("%s parsed storage benchmark data", label))

  emit_table(
    provider_resolved_config(provider),
    sprintf("%s resolved report configuration", label),
    provider = provider
  )

  scenario_table <- provider_query(provider, "
  select run_id, scenario_name, benchmark_machine_type, benchmark_availability_zone,
         os_tuning, access_mode, storage_targets_raw,
         storage_local_filesystem, storage_block_filesystem, block_volume_performance_class,
         block_volume_type, block_volume_iops, block_volume_throughput_mbps
  from scenarios
  where provider = {provider_literal}
  order by run_id, scenario_name
  ")
  emit_table(scenario_table, sprintf("%s scenario coverage", label), provider = provider)

  dimension_coverage <- provider_query(provider, "
  select benchmark_machine_type, block_volume_performance_class, block_volume_type, block_volume_iops, block_volume_throughput_mbps,
         storage_target, storage_target_filesystem,
         benchmark_rw_mode, io_engine, block_size, iodepth, numjobs,
         durability_mode, durability_every_ops,
         iodepth * numjobs as effective_concurrency,
         sum(case when valid_measurement then 1 else 0 end) as valid_repetitions
  from fio_all
  where provider = {provider_literal}
  group by 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15
  order by 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15
  ")
  emit_table(dimension_coverage, sprintf("%s coverage by explicit analysis dimensions", label), provider = provider)

  emit_heading(2, "Throughput")
  cat("Throughput is reported as MiB/s using `primary_bw_bytes_per_sec`. ", filter_text(provider, "throughput"), "\n\n", sep = "")

  emit_heading(3, "Instance Type Impact")
  emit_heading(4, "Block Storage")
  throughput_instance <- provider_query(provider, glue::glue("
  select benchmark_machine_type, benchmark_rw_mode,
         primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_volume_performance_class = {quote_sql(cfg$instance_comparison_block_performance_class)}
    and io_engine = {quote_sql(cfg$throughput_reference_io_engine)}
    and block_size = {quote_sql(cfg$throughput_reference_block_size)}
    and iodepth = {cfg$throughput_reference_iodepth}
    and numjobs = {cfg$throughput_reference_numjobs}
  "))
  print(metric_box(throughput_instance, "benchmark_machine_type", "bw_mib_per_sec", provider, "benchmark_machine_type", title = sprintf("%s block storage throughput by instance type", label), ylab = "Throughput (MiB/s)"))
  cat("\n\n")

  emit_heading(4, "Local Storage")
  throughput_instance_local <- provider_query(provider, glue::glue("
  select benchmark_machine_type, benchmark_rw_mode,
         primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and storage_target = 'local'
    and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}
    and block_volume_performance_class = {quote_sql(cfg$local_instance_comparison_block_performance_class)}
    and benchmark_rw_mode = {quote_sql(cfg$local_instance_rw_mode)}
    and io_engine = {quote_sql(cfg$throughput_reference_io_engine)}
    and block_size = {quote_sql(cfg$throughput_reference_block_size)}
    and iodepth = {cfg$throughput_reference_iodepth}
    and numjobs = {cfg$throughput_reference_numjobs}
  "))
  print(metric_box(throughput_instance_local, "benchmark_machine_type", "bw_mib_per_sec", provider, "benchmark_machine_type", title = sprintf("%s local storage throughput by instance type", label), ylab = "Throughput (MiB/s)", ncol = 1))
  cat("\n\n")

  emit_heading(3, "Block Storage Performance Class Impact")
  render_performance_class_plots_provider(provider, "primary_bw_bytes_per_sec / 1024.0 / 1024.0", "Throughput (MiB/s)", "throughput", cfg$throughput_reference_block_size, cfg$throughput_reference_iodepth, cfg$throughput_reference_io_engine, cfg$throughput_reference_numjobs)

  emit_heading(3, "Storage Target Impact")
  throughput_target <- provider_query(provider, glue::glue("
  select storage_target, benchmark_rw_mode,
         primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and (
      (storage_target = 'local' and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}) or
      (storage_target = 'block' and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)})
    )
    and io_engine = {quote_sql(cfg$throughput_reference_io_engine)}
    and block_size = {quote_sql(cfg$throughput_reference_block_size)}
    and iodepth = {cfg$throughput_reference_iodepth}
    and numjobs = {cfg$throughput_reference_numjobs}
  "))
  print(metric_box(throughput_target, "storage_target", "bw_mib_per_sec", provider, "storage_target", title = sprintf("%s throughput by storage target", label), ylab = "Throughput (MiB/s)"))
  cat("\n\n")

  emit_heading(3, "Execution Configuration Impact")
  throughput_execution_config <- provider_query(provider, glue::glue("
  select concat(io_engine, ' / q', cast(iodepth as varchar), ' / jobs=', cast(numjobs as varchar)) as execution_config,
         benchmark_rw_mode,
         primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$throughput_reference_block_size)}
  order by case when io_engine = 'io_uring' then 1 else 2 end, iodepth, numjobs
  "))
  print(metric_box(throughput_execution_config, "execution_config", "bw_mib_per_sec", provider, "execution_config", title = sprintf("%s throughput by execution configuration", label), ylab = "Throughput (MiB/s)"))
  cat("\n\n")

  emit_heading(4, "io_uring Queue Depth")
  throughput_iouring_iodepth <- provider_query(provider, glue::glue("
  select concat('q', cast(iodepth as varchar)) as iodepth_config, benchmark_rw_mode,
         primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$throughput_reference_block_size)}
    and io_engine = {quote_sql(cfg$throughput_reference_io_engine)}
    and numjobs = {cfg$throughput_reference_numjobs}
  "))
  print(metric_box(throughput_iouring_iodepth, "iodepth_config", "bw_mib_per_sec", provider, "iodepth_config", title = sprintf("%s io_uring throughput by queue depth", label), ylab = "Throughput (MiB/s)"))
  cat("\n\n")

  emit_heading(4, "psync Worker Count")
  throughput_psync_numjobs <- provider_query(provider, glue::glue("
  select concat('jobs=', cast(numjobs as varchar)) as numjobs_config, benchmark_rw_mode,
         primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$throughput_reference_block_size)}
    and io_engine = 'psync'
    and iodepth = {cfg$psync_iodepth}
  "))
  print(metric_box(throughput_psync_numjobs, "numjobs_config", "bw_mib_per_sec", provider, "numjobs_config", title = sprintf("%s psync throughput by worker count", label), ylab = "Throughput (MiB/s)"))
  cat("\n\n")

  emit_heading(3, "Block Size Impact")
  emit_heading(4, "Block Storage")
  throughput_block_size <- provider_query(provider, glue::glue("
  select block_size, benchmark_rw_mode,
         primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and io_engine = {quote_sql(cfg$throughput_reference_io_engine)}
    and numjobs = {cfg$throughput_reference_numjobs}
    and exists (
      select 1
      from (values {block_size_comparison_values_sql}) as comparison(block_size, iodepth)
      where comparison.block_size = fio.block_size
        and comparison.iodepth = fio.iodepth
    )
  "))
  print(metric_box(throughput_block_size, "block_size", "bw_mib_per_sec", provider, "block_size", title = sprintf("%s block storage throughput by block size", label), ylab = "Throughput (MiB/s)"))
  cat("\n\n")

  emit_heading(4, "Local Storage")
  throughput_block_size_local <- provider_query(provider, glue::glue("
  select block_size, benchmark_rw_mode,
         primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'local'
    and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}
    and io_engine = {quote_sql(cfg$throughput_reference_io_engine)}
    and numjobs = {cfg$throughput_reference_numjobs}
    and exists (
      select 1
      from (values {block_size_comparison_values_sql}) as comparison(block_size, iodepth)
      where comparison.block_size = fio.block_size
        and comparison.iodepth = fio.iodepth
    )
  "))
  print(metric_box(throughput_block_size_local, "block_size", "bw_mib_per_sec", provider, "block_size", title = sprintf("%s local storage throughput by block size", label), ylab = "Throughput (MiB/s)"))
  cat("\n\n")

  emit_heading(3, "Filesystem Impact")
  emit_heading(4, "Block Storage")
  render_filesystem_plot(provider, "block", "primary_bw_bytes_per_sec / 1024.0 / 1024.0", sprintf("%s block storage throughput by filesystem", label), "Throughput (MiB/s)", cfg$throughput_reference_block_size, cfg$throughput_reference_iodepth, cfg$throughput_reference_io_engine, cfg$throughput_reference_numjobs)
  emit_heading(4, "Local Storage")
  render_filesystem_plot(provider, "local", "primary_bw_bytes_per_sec / 1024.0 / 1024.0", sprintf("%s local storage throughput by filesystem", label), "Throughput (MiB/s)", cfg$throughput_reference_block_size, cfg$throughput_reference_iodepth, cfg$throughput_reference_io_engine, cfg$throughput_reference_numjobs)

  emit_heading(3, "Durability Impact")
  cat(sprintf(
    "Durability impact is rendered for write workloads only. These plots keep provider, machine type, performance class, filesystem, and OS tuning fixed and compare `none`, `fsync/N`, and `fdatasync/N` using io_engine = %s, block_size = %s, iodepth = %s, numjobs = %s.\n\n",
    cfg$durability_reference_io_engine,
    cfg$durability_reference_block_size,
    cfg$durability_reference_iodepth,
    cfg$durability_reference_numjobs
  ))
  emit_heading(4, "Block Storage")
  render_durability_plot(provider, "block", "primary_bw_bytes_per_sec / 1024.0 / 1024.0", sprintf("%s block storage throughput by durability", label), "Throughput (MiB/s)", cfg$durability_reference_block_size, cfg$durability_reference_iodepth, cfg$durability_reference_io_engine, cfg$durability_reference_numjobs)
  emit_heading(4, "Local Storage")
  render_durability_plot(provider, "local", "primary_bw_bytes_per_sec / 1024.0 / 1024.0", sprintf("%s local storage throughput by durability", label), "Throughput (MiB/s)", cfg$durability_reference_block_size, cfg$durability_reference_iodepth, cfg$durability_reference_io_engine, cfg$durability_reference_numjobs)

  emit_heading(2, "IOPS")
  cat("IOPS is reported using `primary_iops`. ", filter_text(provider, "iops"), "\n\n", sep = "")

  emit_heading(3, "Instance Type Impact")
  emit_heading(4, "Block Storage")
  iops_instance <- provider_query(provider, glue::glue("
  select benchmark_machine_type, benchmark_rw_mode, primary_iops as iops
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_volume_performance_class = {quote_sql(cfg$instance_comparison_block_performance_class)}
    and io_engine = {quote_sql(cfg$iops_reference_io_engine)}
    and block_size = {quote_sql(cfg$iops_reference_block_size)}
    and iodepth = {cfg$iops_reference_iodepth}
    and numjobs = {cfg$iops_reference_numjobs}
  "))
  print(metric_box(iops_instance, "benchmark_machine_type", "iops", provider, "benchmark_machine_type", title = sprintf("%s block storage IOPS by instance type", label), ylab = "IOPS"))
  cat("\n\n")

  emit_heading(4, "Local Storage")
  iops_instance_local <- provider_query(provider, glue::glue("
  select benchmark_machine_type, benchmark_rw_mode, primary_iops as iops
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and storage_target = 'local'
    and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}
    and block_volume_performance_class = {quote_sql(cfg$local_instance_comparison_block_performance_class)}
    and benchmark_rw_mode = {quote_sql(cfg$local_instance_rw_mode)}
    and io_engine = {quote_sql(cfg$iops_reference_io_engine)}
    and block_size = {quote_sql(cfg$iops_reference_block_size)}
    and iodepth = {cfg$iops_reference_iodepth}
    and numjobs = {cfg$iops_reference_numjobs}
  "))
  print(metric_box(iops_instance_local, "benchmark_machine_type", "iops", provider, "benchmark_machine_type", title = sprintf("%s local storage IOPS by instance type", label), ylab = "IOPS", ncol = 1))
  cat("\n\n")

  emit_heading(3, "Block Storage Performance Class Impact")
  render_performance_class_plots_provider(provider, "primary_iops", "IOPS", "IOPS", cfg$iops_reference_block_size, cfg$iops_reference_iodepth, cfg$iops_reference_io_engine, cfg$iops_reference_numjobs)

  emit_heading(3, "Execution Configuration Impact")
  iops_execution_config <- provider_query(provider, glue::glue("
  select concat(io_engine, ' / q', cast(iodepth as varchar), ' / jobs=', cast(numjobs as varchar)) as execution_config,
         benchmark_rw_mode, primary_iops as iops
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$iops_reference_block_size)}
  order by case when io_engine = 'io_uring' then 1 else 2 end, iodepth, numjobs
  "))
  print(metric_box(iops_execution_config, "execution_config", "iops", provider, "execution_config", title = sprintf("%s IOPS by execution configuration", label), ylab = "IOPS"))
  cat("\n\n")

  emit_heading(4, "io_uring Queue Depth")
  iops_iouring_iodepth <- provider_query(provider, glue::glue("
  select concat('q', cast(iodepth as varchar)) as iodepth_config, benchmark_rw_mode, primary_iops as iops
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$iops_reference_block_size)}
    and io_engine = {quote_sql(cfg$iops_reference_io_engine)}
    and numjobs = {cfg$iops_reference_numjobs}
  "))
  print(metric_box(iops_iouring_iodepth, "iodepth_config", "iops", provider, "iodepth_config", title = sprintf("%s io_uring IOPS by queue depth", label), ylab = "IOPS"))
  cat("\n\n")

  emit_heading(4, "psync Worker Count")
  iops_psync_numjobs <- provider_query(provider, glue::glue("
  select concat('jobs=', cast(numjobs as varchar)) as numjobs_config, benchmark_rw_mode, primary_iops as iops
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$iops_reference_block_size)}
    and io_engine = 'psync'
    and iodepth = {cfg$psync_iodepth}
  "))
  print(metric_box(iops_psync_numjobs, "numjobs_config", "iops", provider, "numjobs_config", title = sprintf("%s psync IOPS by worker count", label), ylab = "IOPS"))
  cat("\n\n")

  emit_heading(3, "Block Size Impact")
  emit_heading(4, "Block Storage")
  iops_block_size <- provider_query(provider, glue::glue("
  select block_size, benchmark_rw_mode, primary_iops as iops
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and io_engine = {quote_sql(cfg$iops_reference_io_engine)}
    and numjobs = {cfg$iops_reference_numjobs}
    and exists (
      select 1
      from (values {block_size_comparison_values_sql}) as comparison(block_size, iodepth)
      where comparison.block_size = fio.block_size
        and comparison.iodepth = fio.iodepth
    )
  "))
  print(metric_box(iops_block_size, "block_size", "iops", provider, "block_size", title = sprintf("%s block storage IOPS by block size", label), ylab = "IOPS"))
  cat("\n\n")

  emit_heading(4, "Local Storage")
  iops_block_size_local <- provider_query(provider, glue::glue("
  select block_size, benchmark_rw_mode, primary_iops as iops
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'local'
    and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}
    and io_engine = {quote_sql(cfg$iops_reference_io_engine)}
    and numjobs = {cfg$iops_reference_numjobs}
    and exists (
      select 1
      from (values {block_size_comparison_values_sql}) as comparison(block_size, iodepth)
      where comparison.block_size = fio.block_size
        and comparison.iodepth = fio.iodepth
    )
  "))
  print(metric_box(iops_block_size_local, "block_size", "iops", provider, "block_size", title = sprintf("%s local storage IOPS by block size", label), ylab = "IOPS"))
  cat("\n\n")

  emit_heading(3, "Storage Target Impact")
  iops_target <- provider_query(provider, glue::glue("
  select storage_target, benchmark_rw_mode, primary_iops as iops
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and (
      (storage_target = 'local' and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}) or
      (storage_target = 'block' and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)})
    )
    and io_engine = {quote_sql(cfg$iops_reference_io_engine)}
    and block_size = {quote_sql(cfg$iops_reference_block_size)}
    and iodepth = {cfg$iops_reference_iodepth}
    and numjobs = {cfg$iops_reference_numjobs}
  "))
  print(metric_box(iops_target, "storage_target", "iops", provider, "storage_target", title = sprintf("%s IOPS by storage target", label), ylab = "IOPS"))
  cat("\n\n")

  emit_heading(3, "Filesystem Impact")
  emit_heading(4, "Block Storage")
  render_filesystem_plot(provider, "block", "primary_iops", sprintf("%s block storage IOPS by filesystem", label), "IOPS", cfg$iops_reference_block_size, cfg$iops_reference_iodepth, cfg$iops_reference_io_engine, cfg$iops_reference_numjobs)
  emit_heading(4, "Local Storage")
  render_filesystem_plot(provider, "local", "primary_iops", sprintf("%s local storage IOPS by filesystem", label), "IOPS", cfg$iops_reference_block_size, cfg$iops_reference_iodepth, cfg$iops_reference_io_engine, cfg$iops_reference_numjobs)

  emit_heading(3, "Durability Impact")
  emit_heading(4, "Block Storage")
  render_durability_plot(provider, "block", "primary_iops", sprintf("%s block storage IOPS by durability", label), "IOPS", cfg$durability_reference_block_size, cfg$durability_reference_iodepth, cfg$durability_reference_io_engine, cfg$durability_reference_numjobs)
  emit_heading(4, "Local Storage")
  render_durability_plot(provider, "local", "primary_iops", sprintf("%s local storage IOPS by durability", label), "IOPS", cfg$durability_reference_block_size, cfg$durability_reference_iodepth, cfg$durability_reference_io_engine, cfg$durability_reference_numjobs)

  emit_heading(2, "Latency")
  cat("Latency is reported in microseconds. ", filter_text(provider, "latency"), "\n\n", sep = "")

  emit_heading(3, "Latency Metric Overview")
  latency_metric_overview <- provider_query(provider, glue::glue("
  select benchmark_rw_mode, 'avg' as latency_metric, primary_clat_mean_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  union all
  select benchmark_rw_mode, 'p50' as latency_metric, primary_clat_p50_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  union all
  select benchmark_rw_mode, 'p99' as latency_metric, primary_clat_p99_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  union all
  select benchmark_rw_mode, 'p99.9' as latency_metric, primary_clat_p999_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  "))
  print(metric_box(latency_metric_overview, "latency_metric", "latency_us", provider, "latency_metric", title = sprintf("%s latency distribution by metric", label), ylab = "Latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(3, "Instance Type Impact")
  emit_heading(4, "Block Storage")
  emit_heading(5, "P99")
  latency_instance <- provider_query(provider, glue::glue("
  select benchmark_machine_type, benchmark_rw_mode,
         primary_clat_p99_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_volume_performance_class = {quote_sql(cfg$instance_comparison_block_performance_class)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  "))
  print(metric_box(latency_instance, "benchmark_machine_type", "latency_us", provider, "benchmark_machine_type", title = sprintf("%s block storage P99 latency by instance type", label), ylab = "P99 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(5, "P50")
  latency_instance_p50 <- provider_query(provider, glue::glue("
  select benchmark_machine_type, benchmark_rw_mode,
         primary_clat_p50_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_volume_performance_class = {quote_sql(cfg$instance_comparison_block_performance_class)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  "))
  print(metric_box(latency_instance_p50, "benchmark_machine_type", "latency_us", provider, "benchmark_machine_type", title = sprintf("%s block storage P50 latency by instance type", label), ylab = "P50 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(4, "Local Storage")
  emit_heading(5, "P99")
  latency_instance_local <- provider_query(provider, glue::glue("
  select benchmark_machine_type, benchmark_rw_mode,
         primary_clat_p99_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and storage_target = 'local'
    and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}
    and block_volume_performance_class = {quote_sql(cfg$local_instance_comparison_block_performance_class)}
    and benchmark_rw_mode = {quote_sql(cfg$local_instance_rw_mode)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  "))
  print(metric_box(latency_instance_local, "benchmark_machine_type", "latency_us", provider, "benchmark_machine_type", title = sprintf("%s local storage P99 latency by instance type", label), ylab = "P99 latency (us)", y_zero = FALSE, ncol = 1))
  cat("\n\n")

  emit_heading(5, "P50")
  latency_instance_local_p50 <- provider_query(provider, glue::glue("
  select benchmark_machine_type, benchmark_rw_mode,
         primary_clat_p50_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and storage_target = 'local'
    and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}
    and block_volume_performance_class = {quote_sql(cfg$local_instance_comparison_block_performance_class)}
    and benchmark_rw_mode = {quote_sql(cfg$local_instance_rw_mode)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  "))
  print(metric_box(latency_instance_local_p50, "benchmark_machine_type", "latency_us", provider, "benchmark_machine_type", title = sprintf("%s local storage P50 latency by instance type", label), ylab = "P50 latency (us)", y_zero = FALSE, ncol = 1))
  cat("\n\n")

  emit_heading(3, "Block Storage Performance Class Impact")
  emit_heading(4, "P99")
  render_performance_class_plots_provider(provider, "primary_clat_p99_ns / 1000.0", "P99 latency (us)", "P99 latency", cfg$latency_reference_block_size, cfg$latency_reference_iodepth, cfg$latency_reference_io_engine, cfg$latency_reference_numjobs, heading_level = 5, y_zero = FALSE)
  emit_heading(4, "P50")
  render_performance_class_plots_provider(provider, "primary_clat_p50_ns / 1000.0", "P50 latency (us)", "P50 latency", cfg$latency_reference_block_size, cfg$latency_reference_iodepth, cfg$latency_reference_io_engine, cfg$latency_reference_numjobs, heading_level = 5, y_zero = FALSE)

  emit_heading(3, "Execution Configuration Impact")
  emit_heading(4, "P99")
  latency_execution_config <- provider_query(provider, glue::glue("
  select concat(io_engine, ' / q', cast(iodepth as varchar), ' / jobs=', cast(numjobs as varchar)) as execution_config,
         benchmark_rw_mode,
         primary_clat_p99_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
  order by case when io_engine = 'io_uring' then 1 else 2 end, iodepth, numjobs
  "))
  print(metric_box(latency_execution_config, "execution_config", "latency_us", provider, "execution_config", title = sprintf("%s P99 latency by execution configuration", label), ylab = "P99 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(5, "io_uring Queue Depth")
  latency_iouring_iodepth <- provider_query(provider, glue::glue("
  select concat('q', cast(iodepth as varchar)) as iodepth_config, benchmark_rw_mode,
         primary_clat_p99_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and numjobs = {cfg$latency_reference_numjobs}
  "))
  print(metric_box(latency_iouring_iodepth, "iodepth_config", "latency_us", provider, "iodepth_config", title = sprintf("%s io_uring P99 latency by queue depth", label), ylab = "P99 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(5, "psync Worker Count")
  latency_psync_numjobs <- provider_query(provider, glue::glue("
  select concat('jobs=', cast(numjobs as varchar)) as numjobs_config, benchmark_rw_mode,
         primary_clat_p99_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and io_engine = 'psync'
    and iodepth = {cfg$psync_iodepth}
  "))
  print(metric_box(latency_psync_numjobs, "numjobs_config", "latency_us", provider, "numjobs_config", title = sprintf("%s psync P99 latency by worker count", label), ylab = "P99 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(4, "P50")
  latency_execution_config_p50 <- provider_query(provider, glue::glue("
  select concat(io_engine, ' / q', cast(iodepth as varchar), ' / jobs=', cast(numjobs as varchar)) as execution_config,
         benchmark_rw_mode,
         primary_clat_p50_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
  order by case when io_engine = 'io_uring' then 1 else 2 end, iodepth, numjobs
  "))
  print(metric_box(latency_execution_config_p50, "execution_config", "latency_us", provider, "execution_config", title = sprintf("%s P50 latency by execution configuration", label), ylab = "P50 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(5, "io_uring Queue Depth")
  latency_iouring_iodepth_p50 <- provider_query(provider, glue::glue("
  select concat('q', cast(iodepth as varchar)) as iodepth_config, benchmark_rw_mode,
         primary_clat_p50_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and numjobs = {cfg$latency_reference_numjobs}
  "))
  print(metric_box(latency_iouring_iodepth_p50, "iodepth_config", "latency_us", provider, "iodepth_config", title = sprintf("%s io_uring P50 latency by queue depth", label), ylab = "P50 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(5, "psync Worker Count")
  latency_psync_numjobs_p50 <- provider_query(provider, glue::glue("
  select concat('jobs=', cast(numjobs as varchar)) as numjobs_config, benchmark_rw_mode,
         primary_clat_p50_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and io_engine = 'psync'
    and iodepth = {cfg$psync_iodepth}
  "))
  print(metric_box(latency_psync_numjobs_p50, "numjobs_config", "latency_us", provider, "numjobs_config", title = sprintf("%s psync P50 latency by worker count", label), ylab = "P50 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(3, "Block Size Impact")
  emit_heading(4, "Block Storage")
  emit_heading(5, "P99")
  latency_block_size <- provider_query(provider, glue::glue("
  select block_size, benchmark_rw_mode,
         primary_clat_p99_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and numjobs = {cfg$latency_reference_numjobs}
    and exists (
      select 1
      from (values {block_size_comparison_values_sql}) as comparison(block_size, iodepth)
      where comparison.block_size = fio.block_size
        and comparison.iodepth = fio.iodepth
    )
  "))
  print(metric_box(latency_block_size, "block_size", "latency_us", provider, "block_size", title = sprintf("%s block storage P99 latency by block size", label), ylab = "P99 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(5, "P50")
  latency_block_size_p50 <- provider_query(provider, glue::glue("
  select block_size, benchmark_rw_mode,
         primary_clat_p50_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'block'
    and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and numjobs = {cfg$latency_reference_numjobs}
    and exists (
      select 1
      from (values {block_size_comparison_values_sql}) as comparison(block_size, iodepth)
      where comparison.block_size = fio.block_size
        and comparison.iodepth = fio.iodepth
    )
  "))
  print(metric_box(latency_block_size_p50, "block_size", "latency_us", provider, "block_size", title = sprintf("%s block storage P50 latency by block size", label), ylab = "P50 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(4, "Local Storage")
  emit_heading(5, "P99")
  latency_block_size_local <- provider_query(provider, glue::glue("
  select block_size, benchmark_rw_mode,
         primary_clat_p99_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'local'
    and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and numjobs = {cfg$latency_reference_numjobs}
    and exists (
      select 1
      from (values {block_size_comparison_values_sql}) as comparison(block_size, iodepth)
      where comparison.block_size = fio.block_size
        and comparison.iodepth = fio.iodepth
    )
  "))
  print(metric_box(latency_block_size_local, "block_size", "latency_us", provider, "block_size", title = sprintf("%s local storage P99 latency by block size", label), ylab = "P99 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(5, "P50")
  latency_block_size_local_p50 <- provider_query(provider, glue::glue("
  select block_size, benchmark_rw_mode,
         primary_clat_p50_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and storage_target = 'local'
    and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and numjobs = {cfg$latency_reference_numjobs}
    and exists (
      select 1
      from (values {block_size_comparison_values_sql}) as comparison(block_size, iodepth)
      where comparison.block_size = fio.block_size
        and comparison.iodepth = fio.iodepth
    )
  "))
  print(metric_box(latency_block_size_local_p50, "block_size", "latency_us", provider, "block_size", title = sprintf("%s local storage P50 latency by block size", label), ylab = "P50 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(3, "Storage Target Impact")
  emit_heading(4, "P99")
  latency_target <- provider_query(provider, glue::glue("
  select storage_target, benchmark_rw_mode,
         primary_clat_p99_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and (
      (storage_target = 'local' and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}) or
      (storage_target = 'block' and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)})
    )
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  "))
  print(metric_box(latency_target, "storage_target", "latency_us", provider, "storage_target", title = sprintf("%s P99 latency by storage target", label), ylab = "P99 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(4, "P50")
  latency_target_p50 <- provider_query(provider, glue::glue("
  select storage_target, benchmark_rw_mode,
         primary_clat_p50_ns / 1000.0 as latency_us
  from fio
  where provider = {provider_literal}
    and valid_measurement
    and os_tuning = {quote_sql(cfg$reference_os_tuning)}
    and benchmark_machine_type = {quote_sql(cfg$reference_machine_type)}
    and block_volume_performance_class = {quote_sql(cfg$reference_block_performance_class)}
    and (
      (storage_target = 'local' and storage_target_filesystem = {quote_sql(cfg$reference_local_filesystem)}) or
      (storage_target = 'block' and storage_target_filesystem = {quote_sql(cfg$reference_block_filesystem)})
    )
    and io_engine = {quote_sql(cfg$latency_reference_io_engine)}
    and block_size = {quote_sql(cfg$latency_reference_block_size)}
    and iodepth = {cfg$latency_reference_iodepth}
    and numjobs = {cfg$latency_reference_numjobs}
  "))
  print(metric_box(latency_target_p50, "storage_target", "latency_us", provider, "storage_target", title = sprintf("%s P50 latency by storage target", label), ylab = "P50 latency (us)", y_zero = FALSE))
  cat("\n\n")

  emit_heading(3, "Filesystem Impact")
  emit_heading(4, "Block Storage")
  render_filesystem_plot(provider, "block", "primary_clat_p99_ns / 1000.0", sprintf("%s block storage P99 latency by filesystem", label), "P99 latency (us)", cfg$latency_reference_block_size, cfg$latency_reference_iodepth, cfg$latency_reference_io_engine, cfg$latency_reference_numjobs, y_zero = FALSE)
  render_filesystem_plot(provider, "block", "primary_clat_p50_ns / 1000.0", sprintf("%s block storage P50 latency by filesystem", label), "P50 latency (us)", cfg$latency_reference_block_size, cfg$latency_reference_iodepth, cfg$latency_reference_io_engine, cfg$latency_reference_numjobs, y_zero = FALSE)
  emit_heading(4, "Local Storage")
  render_filesystem_plot(provider, "local", "primary_clat_p99_ns / 1000.0", sprintf("%s local storage P99 latency by filesystem", label), "P99 latency (us)", cfg$latency_reference_block_size, cfg$latency_reference_iodepth, cfg$latency_reference_io_engine, cfg$latency_reference_numjobs, y_zero = FALSE)
  render_filesystem_plot(provider, "local", "primary_clat_p50_ns / 1000.0", sprintf("%s local storage P50 latency by filesystem", label), "P50 latency (us)", cfg$latency_reference_block_size, cfg$latency_reference_iodepth, cfg$latency_reference_io_engine, cfg$latency_reference_numjobs, y_zero = FALSE)

  emit_heading(3, "Durability Impact")
  emit_heading(4, "Block Storage")
  emit_heading(5, "P99")
  render_durability_plot(provider, "block", "primary_clat_p99_ns / 1000.0", sprintf("%s block storage P99 latency by durability", label), "P99 latency (us)", cfg$durability_reference_block_size, cfg$durability_reference_iodepth, cfg$durability_reference_io_engine, cfg$durability_reference_numjobs, y_zero = FALSE)
  emit_heading(5, "P50")
  render_durability_plot(provider, "block", "primary_clat_p50_ns / 1000.0", sprintf("%s block storage P50 latency by durability", label), "P50 latency (us)", cfg$durability_reference_block_size, cfg$durability_reference_iodepth, cfg$durability_reference_io_engine, cfg$durability_reference_numjobs, y_zero = FALSE)
  emit_heading(4, "Local Storage")
  emit_heading(5, "P99")
  render_durability_plot(provider, "local", "primary_clat_p99_ns / 1000.0", sprintf("%s local storage P99 latency by durability", label), "P99 latency (us)", cfg$durability_reference_block_size, cfg$durability_reference_iodepth, cfg$durability_reference_io_engine, cfg$durability_reference_numjobs, y_zero = FALSE)
  emit_heading(5, "P50")
  render_durability_plot(provider, "local", "primary_clat_p50_ns / 1000.0", sprintf("%s local storage P50 latency by durability", label), "P50 latency (us)", cfg$durability_reference_block_size, cfg$durability_reference_iodepth, cfg$durability_reference_io_engine, cfg$durability_reference_numjobs, y_zero = FALSE)

  emit_heading(2, "OS Tuning Coverage")
  tuning_coverage <- provider_query(provider, "
  select os_tuning, count(*) as repetitions
  from fio
  where provider = {provider_literal}
    and valid_measurement
  group by 1
  order by 1
  ")
  emit_table(tuning_coverage, sprintf("%s OS tuning coverage in valid fio repetitions", label), provider = provider)
}
```

# Diagnostics

```{r failures, echo=FALSE}
failure_table <- sql("
select provider, run_id, scenario_name, benchmark_name, storage_target, storage_target_filesystem,
       repetition, fio_error, failure_reason
from failures
order by provider, run_id, scenario_name, benchmark_name, storage_target, repetition
")
if (nrow(failure_table) == 0) {
  cat("No failed fio runs were captured.")
} else {
  knitr::kable(failure_table, caption = "Failed fio repetitions")
}
```

```{r local-target-coverage, echo=FALSE}
local_summary <- sql("
select provider, benchmark_machine_type, block_volume_performance_class, storage_target,
       storage_target_filesystem, benchmark_rw_mode, io_engine, block_size, iodepth, numjobs,
       durability_mode, durability_every_ops,
       iodepth * numjobs as effective_concurrency,
       sum(case when valid_measurement then 1 else 0 end) as valid_repetitions,
       sum(case when not valid_measurement then 1 else 0 end) as invalid_repetitions
from fio_all
where storage_target = 'local'
group by 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13
order by 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13
")
if (nrow(local_summary) == 0) {
  cat("No local-target measurements were parsed.")
} else {
  knitr::kable(local_summary, caption = "Local-target coverage")
}
```
